### 2019-04-18 CV/cv-sections/education.tex
CV

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{MS/PhD in Computer Science } % Degree
{King Abdullah University of Science and Technology} % Institution
{Thuwal, Saudi Arabia} % Location
{Sep. 2018 - PRESENT} % Date(s)
{
}
%------------------------------------------------

\cventry
{BSc in Applied Mathematics and Physics} % Degree
{Moscow Institute of Physics and Technology} % Institution
{Moscow, Russia} % Location
{Sep. 2014 - Jun. 2018} % Date(s)
{ % Description(s) bullet points
}

%------------------------------------------------

\end{cventries}

### 2019-04-18 CV/cv-sections/honors.tex
CV

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Honors \& Awards}

%------------------------------------------------

\begin{cvhonors}

\cvhonor
{Abramov’s Fund Scholarship}
{for top students of Moscow Institute of Physics and Technology}
{Moscow, Russia}
{2015-2017}

\cvhonor
{Honourable Mention} % Award
{APhO (Asian Physics Olympiad)} % Event
{Singapore} % Location
{2014} % Date(s)

\cvhonor
{Prize-Winner} % Award
{All-Russian School Physics Olympiad, Final Round} % Event
{Saint Petersburg, Russia} % Location
{2014} % Date(s)

\cvhonor
{Winner} % Award
{All-Russian School Programming Olympiad, Region Round} % Event
{Moscow, Russia} % Location
{2014} % Date(s)

\cvhonor
{Winner} % Award
{All-Russian School Math Olympiad, Region Round} % Event
{Moscow, Russia} % Location
{2014} % Date(s)

\cvhonor
{Russian President's Scholarship}
{for high school students}
{Russia}
{2012-2014}

\cvhonor
{Moscow Governor’s Scholarship}
{for high school students}
{Moscow, Russia}
{2012-2014}

\cvhonor
{Winner} % Award
{All-Russian School Physics Olympiad, Final Round} % Event
{Vladivostok, Russia} % Location
{2013} % Date(s)

\cvhonor
{Prize-Winner} % Award
{All-Russian School Physics Olympiad, Final Round} % Event
{Saransk, Russia} % Location
{2012} % Date(s)

\end{cvhonors}

### 2019-04-18 CV/cv-sections/papers.tex
CV

\cvsection{Papers}

\begin{cventries}

\cventry
{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik and Sebastian U. Stich} % Role
{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}}
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Samuel Horváth and Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
	\end{cvitems}
}

\cventry
{Alexander Gasnikov, Dmitry Kovalev	} % Role
{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization } % Title
{} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{http://www.mathnet.ru/php/archive.phtml?wshow=paper\&jrnid=crm\&paperid=253\&option\_lang=eng}{
				Computer Research and Modeling, 2018,	Volume 10,	Issue 3,	Pages 305–314}}
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov and Peter Richtárik} % Role
{Stochastic Spectral and Conjugate Descent Methods} % Title
{} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}}
\end{cvitems}
}

\end{cventries}

### 2019-04-18 CV/cv-sections/talks.tex
CV

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Conferences \& Talks}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Talk: <<Stochastic Spectral and Conjugate Descent Methods>>} % Role
{Weekly seminar <<Automatic control and Optimization Theory>>} % Event
{Institute for Control Problems, Moscow, Russia} % Location
{26 Mar. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{http://www.mathnet.ru/php/seminars.phtml?option_lang=rus&presentid=23658}{Link 1}}
		\item {\href{https://www.ipu.ru/node/50794}{Link 2}}
	\end{cvitems}
}

\cventry
{Talk: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}
{Seminar <<Modern Optimization Methods>>}
{Moscow Institute of Physics and Technology, Moscow, Russia}
{25 Mar. 2019}
{
	\begin{cvitems}
		\item {\href{https://vk.com/miptopt?w=wall-132864820_40\%2Fall}{Link}}
	\end{cvitems}
}

\cventry
{Poster Presenter: <<Stochastic Spectral Descent Methods>>} % Role
{Traditional School (Control, Information and Otimization)} % Event
{Voronovo, Moscow Region, Russia} % Location
{Jun. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sites.google.com/site/traditionalschool/}{School website 1}}
		\item {\href{http://ssopt.org}{School website 2}}
	\end{cvitems}
}

\cventry
{Poster Presenter: Stochastic Spectral Descent Methods} % Role
{Optimization and Big Data Workshop} % Event
{KAUST, Thuwal, Saudi Arabia} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://obd.kaust.edu.sa/}{Workshop website}}
		\item {\href{https://epostersonline.com/obd2018/node/51}{Poster}}
	\end{cvitems}
}

%------------------------------------------------

\end{cventries}

### 2019-04-19 main.py
author links

@@ -4,6 +4,12 @@ import markdown
 import dateparser
 import json
 import datetime
+import lxml.html
+import lxml.html.builder
+import json
+
+author_list = json.load(open('authors.json'))
+
 
 class Link:
     def __init__(self, title, href):
@@ -26,14 +32,12 @@ class Paper:
         for key in links:
             self.links.append(Link(key, links[key]))
         
-        authors = meta['authors']
-        self.authors = authors[0]
-        for a in authors[1:-1]:
-            self.authors += ", " + a
-
-        if len(authors) > 1:
-            self.authors += " and " + authors[-1]
-        
+        self.authors = []
+        for a in meta['authors']:
+            if a in author_list:
+                self.authors.append(lxml.html.tostring(lxml.html.builder.A(a, href = author_list[a])).decode())
+            else:
+                self.authors.append(a)
 
 class Post:
     def __init__(self, id, content):
@@ -91,5 +95,4 @@ template = env.get_template('template_index.html')
 
 output = template.render(papers=paper_list, posts=post_list, year=str(datetime.datetime.now().year))
 open('index.html', 'w').write(output)
-
 

### 2019-05-30 CV/cv-sections/papers.tex
CV update

@@
 \begin{cventries}
+
+\cventry
+{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Role
+{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
+{} % Location
+{May 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/1905.11768}{arXiv 2019}}
+	\end{cvitems}
+}
+
+\cventry
+{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
+{Revisiting Stochastic Extragradient} % Title
+{} % Location
+{May 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
+	\end{cvitems}
+}
+
+\cventry
+{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Role
+{RSN: Randomized Subspace Newton} % Title
+{} % Location
+{May 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/1905.10874}{arXiv 2019}}
+	\end{cvitems}
+}
 

### 2019-05-30 CV/cv-sections/papers.tex
-

@@
 \cventry
-{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik and Sebastian U. Stich} % Role
+{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik, Sebastian U. Stich} % Role
 {Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
@@
 \cventry
-{Dmitry Kovalev, Samuel Horváth and Peter Richtárik} % Role
+{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
 {Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
@@
 \cventry
-{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov and Peter Richtárik} % Role
+{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov, Peter Richtárik} % Role
 {Stochastic Spectral and Conjugate Descent Methods} % Title

### 2019-12-10 CV/cv-sections/papers.tex
CV update

@@
 \begin{cventries}
+
+\cventry
+{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
+{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
+{} % Location
+{Dec. 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://drive.google.com/file/d/12aISV2e5XZGDxkr_wg9ILoC27HqoYJsV/view}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
+	\end{cvitems}
+}
+
+\cventry
+{Mohammad Alkousa, Darina Dvinskikh, Fedor Stonyakin, Alexander Gasnikov, Dmitry Kovalev} % Role
+{Accelerated methods for composite non-bilinear saddle point problem} % Title
+{} % Location
+{Dec. 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/1906.03620}{arXiv 2019}}
+	\end{cvitems}
+}
 
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1905.11768}{arXiv 2019}}
+		\item {\href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{NeurIPS 2019}}
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1905.10874}{arXiv 2019}}
+		\item {\href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{NeurIPS 2019}}
 	\end{cvitems}

### 2019-12-10 CV/cv-sections/talks.tex
CV update

@@
 
-%------------------------------------------------
+\cventry
+{Talk: <<Revisiting Stochastic Extragradient Method>>} % Role
+{\href{https://iccopt2019.berlin/index.php}{ICCOPT 2019}} % Event
+{TU, Berlin, Germany} % Location
+{5 Aug. 2019} % Date(s)
+{
+}
+
+\cventry
+{\href{https://2019.ds3-datascience-polytechnique.fr/wp-content/uploads/2019/06/DS3-608_2019.pdf}{Poster: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}} % Role
+{\href{https://2019.ds3-datascience-polytechnique.fr}{Data Science Summer School 2019}} % Event
+{École polytechnique, Paris, France} % Location
+{26 Jun. 2019} % Date(s)
+{
+}
+
+\cventry
+{Poster: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>} % Role
+{\href{http://ssopt.org}{Traditional School (Control, Information and Otimization)}} % Event
+{Voronovo, Moscow Region, Russia} % Location
+{20 Jun. 2019} % Date(s)
+{
+}
 
@@
 {Talk: <<Stochastic Spectral and Conjugate Descent Methods>>} % Role
-{Weekly seminar <<Automatic control and Optimization Theory>>} % Event
-{Institute for Control Problems, Moscow, Russia} % Location
+{\href{https://www.ipu.ru/node/50794}{Weekly seminar <<Automatic control and Optimization Theory>>}} % Event
+{IPU, Moscow, Russia} % Location
 {26 Mar. 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{http://www.mathnet.ru/php/seminars.phtml?option_lang=rus&presentid=23658}{Link 1}}
-		\item {\href{https://www.ipu.ru/node/50794}{Link 2}}
-	\end{cvitems}
+{
 }
@@
 {Talk: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}
-{Seminar <<Modern Optimization Methods>>}
-{Moscow Institute of Physics and Technology, Moscow, Russia}
+{\href{https://vk.com/miptopt?w=wall-132864820_40\%2Fall}{Seminar <<Modern Optimization Methods>>}}
+{MIPT, Moscow, Russia}
 {25 Mar. 2019}
 {
-	\begin{cvitems}
-		\item {\href{https://vk.com/miptopt?w=wall-132864820_40\%2Fall}{Link}}
-	\end{cvitems}
 }
@@
 \cventry
-{Poster Presenter: <<Stochastic Spectral Descent Methods>>} % Role
-{Traditional School (Control, Information and Otimization)} % Event
+{Poster: <<Stochastic Spectral Descent Methods>>} % Role
+{\href{https://sites.google.com/site/traditionalschool/}{Traditional School (Control, Information and Otimization)}} % Event
 {Voronovo, Moscow Region, Russia} % Location
 {Jun. 2018} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://sites.google.com/site/traditionalschool/}{School website 1}}
-		\item {\href{http://ssopt.org}{School website 2}}
-	\end{cvitems}
+{
 }
@@
 \cventry
-{Poster Presenter: Stochastic Spectral Descent Methods} % Role
-{Optimization and Big Data Workshop} % Event
+{\href{https://epostersonline.com/obd2018/node/51}{Poster: Stochastic Spectral Descent Methods}} % Role
+{\href{https://obd.kaust.edu.sa/}{Optimization and Big Data Workshop}} % Event
 {KAUST, Thuwal, Saudi Arabia} % Location
 {Feb. 2018} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://obd.kaust.edu.sa/}{Workshop website}}
-		\item {\href{https://epostersonline.com/obd2018/node/51}{Poster}}
-	\end{cvitems}
+{
 }

### 2019-12-10 CV/cv-sections/papers.tex
site update

@@
 	\begin{cvitems}
-		\item {\href{https://drive.google.com/file/d/12aISV2e5XZGDxkr_wg9ILoC27HqoYJsV/view}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
+		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
+		\item {\href{https://arxiv.org/pdf/1912.01597.pdf}{arXiv 2019}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
+		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
 		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}

### 2020-01-12 CV/cv-sections/education.tex
cv update, site update

@@
 \cventry
-{MS/PhD in Computer Science } % Degree
+{PhD in Computer Science } % Degree
 {King Abdullah University of Science and Technology} % Institution
 {Thuwal, Saudi Arabia} % Location
-{Sep. 2018 - PRESENT} % Date(s)
+{Jan. 2020 - PRESENT} % Date(s)
 {
 }
-%------------------------------------------------
+
+\cventry
+{MS in Computer Science } % Degree
+{King Abdullah University of Science and Technology} % Institution
+{Thuwal, Saudi Arabia} % Location
+{Sep. 2018 - Dec. 2019} % Date(s)
+{
+}
 

### 2020-05-05 CV/cv-sections/papers.tex
cv update, site update
cv update
added new papers

@@
 \begin{cventries}
+
+\cventry
+{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Role
+{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
+{} % Location
+{Apr. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/pdf/2004.01442.pdf}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Role
+{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
+{} % Location
+{Feb. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/pdf/2002.11364.pdf}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Role
+{Fast Linear Convergence of Randomized BFGS} % Title
+{} % Location
+{Feb. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/pdf/2002.11337.pdf}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Role
+{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
+{} % Location
+{Feb. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/pdf/2002.04670.pdf}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Role
+{Distributed Fixed Point Methods with Compressed Iterates} % Title
+{} % Location
+{Dec. 2019} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/pdf/1912.09925.pdf}{arXiv 2019}}		
+	\end{cvitems}
+}
 
@@
 		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
+		\item Accepted to AISTATS 2020
 	\end{cvitems}
@@
 		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
+		\item Ассepted to ALT 2020
 	\end{cvitems}

### 2020-11-18 CV/cv-sections/papers.tex
CV update

@@
 \begin{cventries}
+
+\cventry
+{Dmitry Kovalev, Anastasia Koloskova, Martin Jaggi, Peter Richtarik, Sebastian U. Stich} % Role
+{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} % Title
+{} % Location
+{Nov. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/2011.01697}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Eduard Gorbunov, Dmitry Kovalev, Dmitry Makarenko, Peter Richtárik} % Role
+{Linearly Converging Error Compensated SGD} % Title
+{} % Location
+{Oct. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{NeurIPS 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin} % Role
+{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} % Title
+{} % Location
+{Sep. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://arxiv.org/abs/2009.11069}{arXiv 2020}}		
+	\end{cvitems}
+}
+
+\cventry
+{Dmitry Kovalev, Adil Salim, Peter Richtárik} % Role
+{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} % Title
+{} % Location
+{Jun. 2020} % Date(s)
+{ % Description(s)
+	\begin{cvitems}
+		\item {\href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{NeurIPS 2020}}		
+	\end{cvitems}
+}
 
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/pdf/2004.01442.pdf}{arXiv 2020}}		
+		\item {\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/pdf/2002.11364.pdf}{arXiv 2020}}		
+		\item {\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/pdf/2002.11337.pdf}{arXiv 2020}}		
+		\item {\href{https://arxiv.org/abs/2002.11337}{arXiv 2020}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/pdf/2002.04670.pdf}{arXiv 2020}}		
+		\item {\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/pdf/1912.09925.pdf}{arXiv 2019}}		
+		\item {\href{https://arxiv.org/abs/1912.09925}{arXiv 2019}}		
 	\end{cvitems}
@@
 		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
-		\item {\href{https://arxiv.org/pdf/1912.01597.pdf}{arXiv 2019}}		
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
-		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
-		\item Accepted to AISTATS 2020
+		\item {\href{http://proceedings.mlr.press/v108/mishchenko20a}{AISTATS 2020}}
 	\end{cvitems}
@@
 	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
-		\item Ассepted to ALT 2020
+		\item {\href{http://proceedings.mlr.press/v117/kovalev20a}{ALT 2020}}
 	\end{cvitems}

### 2020-11-18 CV/cv-sections/education.tex
CV small update

@@
 \cventry
-{BSc in Applied Mathematics and Physics} % Degree
+{BS in Applied Mathematics and Physics} % Degree
 {Moscow Institute of Physics and Technology} % Institution

### 2021-02-27 main.py
style update

@@ -25,6 +25,8 @@ class Paper:
         self._id = id
         self._date = dateparser.parse(meta['date'][0])
 
+        self.date = self._date.strftime("%d %b %Y")
+
         self.title = meta['title'][0]
         
         links = json.loads(meta['links'][0])
@@ -51,7 +53,7 @@ class Post:
         
         self.title = meta['title'][0]
         self.summary = markdown.markdown(meta['summary'][0])
-        self.date = self._date.strftime("%d %b. %Y, %H:%M")
+        self.date = self._date.strftime("%d %b %Y, %H:%M")
         
         if 'links' in meta:
             links = json.loads(meta['links'][0])

### 2021-02-27 CV/cv-sections/papers.tex
-

--- 2019-12-10 CV/cv-sections/papers.tex
@@
 
-\cventry
-{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
-{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
-{} % Location
-{Dec. 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
-		\item {\href{https://arxiv.org/pdf/1912.01597.pdf}{arXiv 2019}}		
-	\end{cvitems}
-}
+%\cventry
+%{} % Authors
+%{} % Title
+%{} 
+%{}
+%{\href{}{}}
 
 \cventry
-{Mohammad Alkousa, Darina Dvinskikh, Fedor Stonyakin, Alexander Gasnikov, Dmitry Kovalev} % Role
-{Accelerated methods for composite non-bilinear saddle point problem} % Title
-{} % Location
-{Dec. 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1906.03620}{arXiv 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Role
-{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
-{} % Location
-{May 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{NeurIPS 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
-{Revisiting Stochastic Extragradient} % Title
-{} % Location
-{May 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
-		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Role
-{RSN: Randomized Subspace Newton} % Title
-{} % Location
-{May 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{NeurIPS 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik, Sebastian U. Stich} % Role
-{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
-{} % Location
-{Jan. 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
-{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
-{} % Location
-{Jan. 2019} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
-	\end{cvitems}
-}
-
-\cventry
-{Alexander Gasnikov, Dmitry Kovalev	} % Role
-{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization } % Title
-{} % Location
-{Feb. 2018} % Date(s)
-{ % Description(s)
-	\begin{cvitems}
-		\item {\href{http://www.mathnet.ru/php/archive.phtml?wshow=paper\&jrnid=crm\&paperid=253\&option\_lang=eng}{
-				Computer Research and Modeling, 2018,	Volume 10,	Issue 3,	Pages 305–314}}
-	\end{cvitems}
-}
-
-\cventry
-{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov, Peter Richtárik} % Role
+{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov, Peter Richtárik} % Authors
 {Stochastic Spectral and Conjugate Descent Methods} % Title
-{} % Location
-{Feb. 2018} % Date(s)
-{ % Description(s)
-\begin{cvitems}
-\item {\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}}
-\end{cvitems}
-}
+{} 
+{Feb 2020}
+{\href{}{}}
 

### 2021-02-27 main.py
-

@@ -37,9 +37,10 @@ class Paper:
         self.authors = []
         for a in meta['authors']:
             if a in author_list:
-                self.authors.append(lxml.html.tostring(lxml.html.builder.A(a, href = author_list[a])).decode())
+                # self.authors.append(lxml.html.tostring(lxml.html.builder.A(a, href = author_list[a])).decode())
+                self.authors.append(Link(a, author_list[a]))
             else:
-                self.authors.append(a)
+                self.authors.append(Link(a, ''))
 
 class Post:
     def __init__(self, id, content):
@@ -53,7 +54,7 @@ class Post:
         
         self.title = meta['title'][0]
         self.summary = markdown.markdown(meta['summary'][0])
-        self.date = self._date.strftime("%d %b %Y, %H:%M")
+        self.date = self._date.strftime("%d %b %Y")
         
         if 'links' in meta:
             links = json.loads(meta['links'][0])

### 2021-02-27 CV/cv-sections/papers.tex
-
CV

@@
 %{} % Title
+%{\href{}{}} 
+%{} % Date
 %{}
-%{}
-%{\href{}{}}
+
+\cventry
+{Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtárik} % Authors
+{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} % Title
+{\href{https://arxiv.org/abs/2102.11079}{arXiv 2021}} 
+{22 Feb 2021} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Alexander Rogozin, Alexander Gasnikov} % Authors
+{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} % Title
+{\href{https://arxiv.org/abs/2102.09234}{arXiv 2021}} 
+{18 Feb 2021} % Date
+{}
+
+\cventry
+{Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtárik} % Authors
+{IntSGD: Floatless Compression of Stochastic Gradients} % Title
+{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 
+{16 Feb 2021} % Date
+{}
+
+\cventry
+{Alexander Rogozin, Alexander Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov} % Authors
+{Decentralized Distributed Optimization for Saddle Point Problems} % Title
+{\href{https://arxiv.org/abs/2102.07758}{arXiv 2021}} 
+{15 Feb 2021} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Anastasia Koloskova, Martin Jaggi, Peter Richtárik, Sebastian U. Stich} % Authors
+{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} % Title
+{AISTATS 2021} 
+{03 Nov 2020} % Date
+{}
+
+\cventry
+{Eduard Gorbunov, Dmitry Kovalev, Dmitry Makarenko , Peter Richtárik} % Authors
+{Linearly Converging Error Compensated SGD} % Title
+{\href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{NeurIPS 2020}} 
+{23 Oct 2020} % Date
+{}
+
+\cventry
+{Alexander Rogozin, Vladislav Lukoshkin , Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin} % Authors
+{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} % Title
+{\href{https://arxiv.org/abs/2009.11069}{arXiv 2020}} 
+{23 Sep 2020} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Adil Salim, Peter Richtárik} % Authors
+{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} % Title
+{\href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{NeurIPS 2020}} 
+{21 Jun 2020} % Date
+{}
+
+\cventry
+{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Authors
+{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
+{\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}} 
+{03 Apr 2020} % Date
+{}
+
+\cventry
+{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Authors
+{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
+{\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}} 
+{26 Feb 2020} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Authors
+{Fast Linear Convergence of Randomized BFGS} % Title
+{\href{https://arxiv.org/abs/2002.11337}{arXiv 2020}} 
+{26 Feb 2020} % Date
+{}
+
+\cventry
+{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Authors
+{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
+{\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}} 
+{11 Feb 2020} % Date
+{}
+
+\cventry
+{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Authors
+{Distributed Fixed Point Methods with Compressed Iterates} % Title
+{\href{https://arxiv.org/abs/1912.09925}{arXiv 2019}} 
+{20 Dec 2019} % Date
+{}
+
+\cventry
+{Mohammad Alkousa, Darina Dvinskikh, Fedor Stonyakin, Alexander Gasnikov, Dmitry Kovalev} % Authors
+{Accelerated methods for composite non-bilinear saddle point problem} % Title
+{\href{https://link.springer.com/article/10.1134/S0965542520110020}{Computational Mathematics and Mathematical Physics 2020}} 
+{09 Dec 2019} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Authors
+{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
+{\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop}} 
+{03 Dec 2019} % Date
+{}
+
+\cventry
+{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Authors
+{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
+{\href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{NeurIPS 2019}} 
+{28 May 2019} % Date
+{}
+
+\cventry
+{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Authors
+{Revisiting Stochastic Extragradient} % Title
+{\href{http://proceedings.mlr.press/v108/mishchenko20a}{AISTATS 2020}} 
+{27 May 2019} % Date
+{}
+
+\cventry
+{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Authors
+{RSN: Randomized Subspace Newton} % Title
+{\href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{NeurIPS 2019}} 
+{26 May 2019} % Date
+{}
+
+\cventry
+{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik, Sebastian U. Stich} % Authors
+{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
+{\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}} 
+{04 Apr 2019} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Authors
+{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
+{\href{http://proceedings.mlr.press/v117/kovalev20a}{ALT 2020}} 
+{24 Jan 2019} % Date
+{}
+
+\cventry
+{Alexander Gasnikov, Dmitry Kovalev} % Authors
+{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization} % Title
+{\href{http://www.mathnet.ru/php/archive.phtml?wshow=paper\&jrnid=crm\&paperid=253\&option\_lang=eng}{
+						Computer Research\linebreak and Modeling  2018}} 
+{28 Feb 2018} % Date
+{}
 
@@
 {Stochastic Spectral and Conjugate Descent Methods} % Title
+{\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}} 
+{11 Feb 2018} % Date
 {}
-{Feb 2020}
-{\href{}{}}
+
+%\cventry
+%{Dmitry Kovalev, Anastasia Koloskova, Martin Jaggi, Peter Richtarik, Sebastian U. Stich} % Role
+%{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} % Title
+%{} % Location
+%{Nov. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/2011.01697}{arXiv 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Eduard Gorbunov, Dmitry Kovalev, Dmitry Makarenko, Peter Richtárik} % Role
+%{Linearly Converging Error Compensated SGD} % Title
+%{} % Location
+%{Oct. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{NeurIPS 2020}}		
+%	\end{cvitems}
+%}	
+%
+%\cventry
+%{Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin} % Role
+%{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} % Title
+%{} % Location
+%{Sep. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/2009.11069}{arXiv 2020}}		
+%	\end{cvitems}
+%}	
+%
+%\cventry
+%{Dmitry Kovalev, Adil Salim, Peter Richtárik} % Role
+%{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} % Title
+%{} % Location
+%{Jun. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{NeurIPS 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%	
+%\cventry
+%{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Role
+%{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
+%{} % Location
+%{Apr. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Role
+%{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
+%{} % Location
+%{Feb. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Role
+%{Fast Linear Convergence of Randomized BFGS} % Title
+%{} % Location
+%{Feb. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/2002.11337}{arXiv 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Role
+%{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
+%{} % Location
+%{Feb. 2020} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Role
+%{Distributed Fixed Point Methods with Compressed Iterates} % Title
+%{} % Location
+%{Dec. 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/1912.09925}{arXiv 2019}}		
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
+%{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
+%{} % Location
+%{Dec. 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
+%	\end{cvitems}
+%}	
+%
+%\cventry
+%{Mohammad Alkousa, Darina Dvinskikh, Fedor Stonyakin, Alexander Gasnikov, Dmitry Kovalev} % Role
+%{Accelerated methods for composite non-bilinear saddle point problem} % Title
+%{} % Location
+%{Dec. 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/1906.03620}{arXiv 2019}}
+%	\end{cvitems}
+%}	
+%
+%\cventry
+%{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Role
+%{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
+%{} % Location
+%{May 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{NeurIPS 2019}}
+%	\end{cvitems}
+%}	
+%	
+%\cventry
+%{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
+%{Revisiting Stochastic Extragradient} % Title
+%{} % Location
+%{May 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{http://proceedings.mlr.press/v108/mishchenko20a}{AISTATS 2020}}
+%	\end{cvitems}
+%}
+%
+%\cventry
+%{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Role
+%{RSN: Randomized Subspace Newton} % Title
+%{} % Location
+%{May 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{NeurIPS 2019}}
+%	\end{cvitems}
+%}
+%
+%\cventry
+%{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik, Sebastian U. Stich} % Role
+%{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
+%{} % Location
+%{Jan. 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}}
+%	\end{cvitems}
+%}
+%
+%\cventry
+%{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
+%{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
+%{} % Location
+%{Jan. 2019} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{http://proceedings.mlr.press/v117/kovalev20a}{ALT 2020}}
+%	\end{cvitems}
+%}
+%
+%
+%\cventry
+%{Alexander Gasnikov, Dmitry Kovalev	} % Role
+%{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization } % Title
+%{} % Location
+%{Feb. 2018} % Date(s)
+%{ % Description(s)
+%	\begin{cvitems}
+%		\item {\href{http://www.mathnet.ru/php/archive.phtml?wshow=paper\&jrnid=crm\&paperid=253\&option\_lang=eng}{
+%				Computer Research and Modeling, 2018,	Volume 10,	Issue 3,	Pages 305–314}}
+%	\end{cvitems}
+%}
+%
+%
+%\cventry
+%{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov, Peter Richtárik} % Role
+%{Stochastic Spectral and Conjugate Descent Methods} % Title
+%{} % Location
+%{Feb. 2018} % Date(s)
+%{ % Description(s)
+%\begin{cvitems}
+%\item {\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}}
+%\end{cvitems}
+%}
 

### 2021-02-28 CV/cv-sections/papers.tex
-

@@
 {From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
-{\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}} 
+{\href{http://proceedings.mlr.press/v119/malinovskiy20a.html}{ICML 2020}} 
 {03 Apr 2020} % Date
@@
 {Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
-{\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}} 
+{\href{http://proceedings.mlr.press/v119/li20g.html}{ICML 2020}} 
 {26 Feb 2020} % Date
@@
 {Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
-{\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}} 
+{\href{http://proceedings.mlr.press/v119/hanzely20b.html}{ICML 2020}} 
 {11 Feb 2020} % Date

### 2021-08-31 CV/cv-sections/honors.tex
CV update
cv update

@@
 \begin{cvhonors}
+\cvhonor
+{\href{http://federated-learning.org/fl-icml-2021/}{Best Student Paper Award}}
+{FL-ICML  2021 Workshop}
+{Online}
+{2021}
+
+\cvhonor
+{\href{https://yandex.ru/scholarships/scholars}{Yandex Ilya Segalovich Scientific Prize}}
+{for young researchers}
+{Moscow, Russia}
+{2021}
+
+\cvhonor
+{\href{https://yandex.ru/scholarships/scholars}{Yandex Ilya Segalovich Scientific Prize}}
+{for young researchers}
+{Moscow, Russia}
+{2020}
 

### 2021-08-31 CV/cv-sections/papers.tex
cv update

@@
 \cventry
+{Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov} % Authors
+{Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} % Title
+{\href{https://arxiv.org/abs/2107.05957}{arXiv 2021}} 
+{13 Jul, 2021} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Elnur Gasanov, Peter Richtárik, Alexander Gasnikov} % Authors
+{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} % Title
+{\href{http://federated-learning.org/fl-icml-2021/}{ICML 2021 Workshop}} 
+{08 Jun 2021} % Date
+{}
+
+\cventry
 {Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtárik} % Authors
@@
 {ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} % Title
-{\href{https://arxiv.org/abs/2102.09234}{arXiv 2021}} 
+{\href{http://proceedings.mlr.press/v139/kovalev21a}{ICML 2021}} 
 {18 Feb 2021} % Date

### 2022-02-22 main.py
migrated to new MacBook

@@ -16,6 +16,7 @@ class Link:
         self.title = title
         self.href = href
 
+
 class Paper:
     def __init__(self, id, content):
         md = markdown.Markdown(extensions=['meta'])
@@ -28,12 +29,12 @@ class Paper:
         self.date = self._date.strftime("%d %b %Y")
 
         self.title = meta['title'][0]
-        
+
         links = json.loads(meta['links'][0])
         self.links = []
         for key in links:
             self.links.append(Link(key, links[key]))
-        
+
         self.authors = []
         for a in meta['authors']:
             if a in author_list:
@@ -41,6 +42,7 @@ class Paper:
                 self.authors.append(Link(a, author_list[a]))
             else:
                 self.authors.append(Link(a, ''))
+
 
 class Post:
     def __init__(self, id, content):
@@ -51,20 +53,20 @@ class Post:
         self._id = id
         self._date = dateparser.parse(meta['date'][0])
 
-        
         self.title = meta['title'][0]
         self.summary = markdown.markdown(meta['summary'][0])
         self.date = self._date.strftime("%d %b %Y")
-        
+
         if 'links' in meta:
             links = json.loads(meta['links'][0])
             self.links = []
             for key in links:
                 self.links.append(Link(key, links[key]))
 
-#-----------
-#LOAD PAPERS
-#-----------
+# -----------
+# LOAD PAPERS
+# -----------
+
 
 paper_list = []
 
@@ -76,9 +78,9 @@ for root, dirs, files in os.walk("papers"):
 
 paper_list.sort(key=lambda p: p._date, reverse=True)
 
-#----------
-#LOAD POSTS
-#----------
+# ----------
+# LOAD POSTS
+# ----------
 
 post_list = []
 
@@ -91,11 +93,10 @@ for root, dirs, files in os.walk("posts"):
 post_list.sort(key=lambda p: p._date, reverse=True)
 
 
-
 file_loader = jinja2.FileSystemLoader('')
 env = jinja2.Environment(loader=file_loader)
 template = env.get_template('template_index.html')
 
-output = template.render(papers=paper_list, posts=post_list, year=str(datetime.datetime.now().year))
+output = template.render(papers=paper_list, posts=post_list,
+                         year=str(datetime.datetime.now().year))
 open('index.html', 'w').write(output)
-

### 2022-02-22 main.py
add papers

@@ -37,6 +37,7 @@ class Paper:
 
         self.authors = []
         for a in meta['authors']:
+            print(a, '/', a[-1])
             if a in author_list:
                 # self.authors.append(lxml.html.tostring(lxml.html.builder.A(a, href = author_list[a])).decode())
                 self.authors.append(Link(a, author_list[a]))

### 2022-02-22 main.py
-

@@ -37,7 +37,6 @@ class Paper:
 
         self.authors = []
         for a in meta['authors']:
-            print(a, '/', a[-1])
             if a in author_list:
                 # self.authors.append(lxml.html.tostring(lxml.html.builder.A(a, href = author_list[a])).decode())
                 self.authors.append(Link(a, author_list[a]))

### 2022-02-22 CV/cv-sections/papers.tex
CV update

--- 2021-02-28 CV/cv-sections/papers.tex
@@
 \cventry
+{Dmitry Kovalev, Aleksandr Beznosikov, Abdurakhmon Sadiev, Michael Persiianov, Peter Richtárik, Alexander Gasnikov} % Authors
+{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} % Title
+{\href{https://arxiv.org/abs/2202.02771}{arXiv 2022}} 
+{06 Feb 2022} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Alexander Gasnikov, Peter Richtárik} % Authors
+{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} % Title
+{\href{https://arxiv.org/abs/2112.15199}{arXiv 2021}} 
+{30 Dec 2021} % Date
+{}
+
+\cventry
+{Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov} % Authors
+{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} % Title
+{\href{https://arxiv.org/abs/2107.05957}{arXiv 2021}} 
+{13 Jul 2021} % Date
+{}
+
+\cventry
+{Dmitry Kovalev, Elnur Gasanov, Peter Richtárik, Alexander Gasnikov} % Authors
+{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} % Title
+{\href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{NeurIPS 2021}} 
+{08 Jun 2021} % Date
+{}
+
+\cventry
 {Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtárik} % Authors

### 2022-03-16 CV/cv-sections/papers.tex
cv update

@@
 {An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} % Title
-{\href{https://arxiv.org/abs/2102.11079}{arXiv 2021}} 
+{\href{http://aistats.org/aistats2022/accepted.html}{AISTATS 2022}}
+%{\href{https://arxiv.org/abs/2102.11079}{arXiv 2021}} 
 {22 Feb 2021} % Date
@@
 {IntSGD: Floatless Compression of Stochastic Gradients} % Title
+{\href{https://openreview.net/forum?id=pFyXqxChZc}{ICLR 2022}}
 {\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 

### 2022-03-18 CV/cv-sections/papers.tex
-

@@
 {\href{https://openreview.net/forum?id=pFyXqxChZc}{ICLR 2022}}
-{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 
+%{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}}
 {16 Feb 2021} % Date

### 2022-03-19 CV2/CV.tex
new cv

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

%!TEX TS-program = xelatex

\documentclass[a4paper,10pt]{article} % Default font size and paper size
\usepackage{fontspec} % For loading fonts
\setmainfont{[Fontin-Regular.otf]}
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont{[Fontin-Regular.otf]} % Main document font
% \setmainfont[SmallCapsFont = Fontin-SmallCaps.otf]{[Fontin-Regular.otf]} % Main document font
\setmainfont{Fontin-Regular.otf}[
BoldFont       = Fontin-Bold.otf ,
ItalicFont     = Fontin-Italic.otf ,
SmallCapsFont  = Fontin-SmallCaps.otf ]

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{tabularx}

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{\centering{\Huge Dmitry Kovalev}\bigskip\par} % Your name

\section{Personal Data}

\begin{tabular}{rl}
\textsc{Phone:} & +7 905 719 06 98\\
\textsc{Email:} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
\textsc{Website:} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
\textsc{Google Scholar:} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
\end{tabular}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabular}{rl}	
\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
&\\
\textsc{2018-2019}& MS in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
&\\
\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
&\\
\textsc{2019-Now}& PhD in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\end{tabular}

\section{Skills}

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}

\begin{tabular}{rl}
\textsc{English} & Advanced Knowledge \\
\textsc{Russian} & Mothertongue\\
\end{tabular}

\section{Awards}

%\begin{itemize}
%	\item \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology, 2021
%	
%	\item \textbf{Best Student Paper Award}, International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021 (FL-ICML'21)
%\end{itemize}
%
%
%
%
%
%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2021
%
%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2020

\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \textbf{Best Student Paper Award}, FL-ICML 2021 Workshop\\
	\textsc{2021} & \textbf{Ilya Segalovich Scientific Prize}, Yandex \\
	\textsc{2020} & \textbf{Ilya Segalovich Scientific Prize}, Yandex\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}

%----------------------------------------------------------------------------------------

% \newpage

% %----------------------------------------------------------------------------------------
% %	GRADE TABLES
% %----------------------------------------------------------------------------------------

% \par{\centering\Large \hypertarget{grds}{Master of Science in \textsc{Finance}}\par}\large{\centering Grades\par}\normalsize

% \begin{center}
% \begin{tabular}{lcc}
% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade}&\textsc{Credit Hrs}\\ \hline
% Corporate Finance (Valuation) & 25 & 6\\
% Financial Statement Analysis & 28 & 6\\
% Statistics & 27 & 6\\
% Theory of Finance & 26 & 6\\
% Quantitative Methods for Finance & 30 & 6\\
% Econometrics & 24 & 6\\
% Derivatives & 31 & 6\\
% Management of Financial and Insurance Companies & 30 & 6\\
% Business Law & 31 & 6\\
% Investment Banking	& 28 & 6\\ \\		
% Behavioral Models for Economics and Finance	 & 29 & 6\\
% Numerical Methods for Finance & 29 & 6\\
% Advanced Derivatives & 30 & 6\\
% Fixed Income (Advanced Methods) & 30 & 6\\ \\
% English Language & 30 &	4\\
% French Language & 31 &	4\\	
% Internship & & 8\\		
% Final Thesis & & 20\\	
% & Total & 120\\\cline{2-3}
% &\textsc{Gpa}&\textbf{8.0}
% \end{tabular}
% \end{center}
% \bigskip
% \hrule
% \bigskip

% %------------------------------------------------

% \bigskip

% \par{\centering\Large \hypertarget{grds_usc}{Exchange Program at \textsc{usc}, Los Angeles}\par}\large{\centering Grades\par}\normalsize

% \begin{center}
% \begin{tabular}{lcc}
% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade} & \textsc{Grade Points}\\ 
% \hline
% Corporate Financial Strategy & A & 4\\
% Derivatives & A & 4\\
% Money, Credit, and Banking & A & 4\\
% Business Strategy & A- & 3.5\\
% & &\\\cline{2-3}
% & \textsc{Gpa} & \textbf{3.875}
% \end{tabular}
% \end{center}

% %----------------------------------------------------------------------------------------

\end{document}

### 2022-03-19 papers.py

@@ -1,0 +1,64 @@
+import jinja2
+import os
+import markdown
+import dateparser
+import json
+import datetime
+import lxml.html
+import lxml.html.builder
+import json
+
+author_list = json.load(open('authors.json'))
+
+
+class Link:
+    def __init__(self, title, href):
+        self.title = title
+        self.href = href
+
+
+class Paper:
+    def __init__(self, id, content):
+        md = markdown.Markdown(extensions=['meta'])
+        md.convert(content)
+        meta = md.Meta
+
+        self._id = id
+        self._date = dateparser.parse(meta['date'][0])
+
+        self.date = self._date.strftime("%d %b %Y")
+
+        self.title = meta['title'][0]
+
+        links = json.loads(meta['links'][0])
+        self.links = []
+        for key in links:
+            self.links.append(Link(key, links[key]))
+
+        self.authors = []
+        for a in meta['authors']:
+            if a in author_list:
+                self.authors.append(Link(a, author_list[a]))
+            else:
+                self.authors.append(Link(a, ''))
+
+# -----------
+# LOAD PAPERS
+# -----------
+
+
+paper_list = []
+
+for root, dirs, files in os.walk("papers"):
+    for name in dirs:
+        input = open(os.path.join(root, name, "index.md"), "r")
+        paper_list.append(Paper(name, input.read()))
+    break
+
+paper_list.sort(key=lambda p: p._date, reverse=True)
+
+print('Papers:')
+for paper in paper_list:
+    print(paper.title)
+    for author in paper.authors:
+        print('\t', author.title, author.href)

### 2022-03-20 CV2/CV.tex
new cv

@@
 \documentclass[a4paper,10pt]{article} % Default font size and paper size
+%\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc}
 \usepackage{fontspec} % For loading fonts
-\setmainfont{[Fontin-Regular.otf]}
+
+%\setmainfont{[Fontin-Regular.otf]}
 \defaultfontfeatures{Mapping=tex-text}
@@
 \begin{tabular}{rl}
-\textsc{Phone:} & +7 905 719 06 98\\
-\textsc{Email:} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
-\textsc{Website:} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
-\textsc{Google Scholar:} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
+\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
+\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
+\textsc{Phone} & +7 905 719 06 98\\
+\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
 \end{tabular}
@@
 \section{Education}
-
 \begin{tabular}{rl}	
@@
 & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-&\\
 \textsc{2018-2019}& MS in Computer Science\\
@@
 & Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-&\\
 \textsc{2018-2021}& MS in Applied Mathematics and Physics\\
@@
 & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-&\\
 \textsc{2019-Now}& PhD in Computer Science\\
@@
 \end{tabular}
+
+\section{Research Interests}
+ Optimization Algorithms, Distributed Optimization, Machine Learning,
 
@@
 \section{Awards}
-
-%\begin{itemize}
-%	\item \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology, 2021
-%	
-%	\item \textbf{Best Student Paper Award}, International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021 (FL-ICML'21)
-%\end{itemize}
-%
-%
-%
-%
-%
-%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2021
-%
-%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2020
-
+\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
 \begin{tabular}{cl}
 	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
-	\textsc{2021} & \textbf{Best Student Paper Award}, FL-ICML 2021 Workshop\\
-	\textsc{2021} & \textbf{Ilya Segalovich Scientific Prize}, Yandex \\
-	\textsc{2020} & \textbf{Ilya Segalovich Scientific Prize}, Yandex\\
+	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
+	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
+	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
 	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
@@
 \end{tabular}
+\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
 
-%----------------------------------------------------------------------------------------
+\newpage
 
-% \newpage
+\section{Papers}
 
-% %----------------------------------------------------------------------------------------
-% %	GRADE TABLES
-% %----------------------------------------------------------------------------------------
-
-% \par{\centering\Large \hypertarget{grds}{Master of Science in \textsc{Finance}}\par}\large{\centering Grades\par}\normalsize
-
-% \begin{center}
-% \begin{tabular}{lcc}
-% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade}&\textsc{Credit Hrs}\\ \hline
-% Corporate Finance (Valuation) & 25 & 6\\
-% Financial Statement Analysis & 28 & 6\\
-% Statistics & 27 & 6\\
-% Theory of Finance & 26 & 6\\
-% Quantitative Methods for Finance & 30 & 6\\
-% Econometrics & 24 & 6\\
-% Derivatives & 31 & 6\\
-% Management of Financial and Insurance Companies & 30 & 6\\
-% Business Law & 31 & 6\\
-% Investment Banking	& 28 & 6\\ \\		
-% Behavioral Models for Economics and Finance	 & 29 & 6\\
-% Numerical Methods for Finance & 29 & 6\\
-% Advanced Derivatives & 30 & 6\\
-% Fixed Income (Advanced Methods) & 30 & 6\\ \\
-% English Language & 30 &	4\\
-% French Language & 31 &	4\\	
-% Internship & & 8\\		
-% Final Thesis & & 20\\	
-% & Total & 120\\\cline{2-3}
-% &\textsc{Gpa}&\textbf{8.0}
-% \end{tabular}
-% \end{center}
-% \bigskip
-% \hrule
-% \bigskip
-
-% %------------------------------------------------
-
-% \bigskip
-
-% \par{\centering\Large \hypertarget{grds_usc}{Exchange Program at \textsc{usc}, Los Angeles}\par}\large{\centering Grades\par}\normalsize
-
-% \begin{center}
-% \begin{tabular}{lcc}
-% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade} & \textsc{Grade Points}\\ 
-% \hline
-% Corporate Financial Strategy & A & 4\\
-% Derivatives & A & 4\\
-% Money, Credit, and Banking & A & 4\\
-% Business Strategy & A- & 3.5\\
-% & &\\\cline{2-3}
-% & \textsc{Gpa} & \textbf{3.875}
-% \end{tabular}
-% \end{center}
-
-% %----------------------------------------------------------------------------------------
+\input{papers.tex}
 

### 2022-03-20 CV2/papers.tex
new cv

\begin{enumerate}
\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint}
\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint}
\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint}
\item \textbf{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{\em \color{black}NeurIPS 2021}
\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint}
\item \textbf{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{http://proceedings.mlr.press/v139/kovalev21a}{\em \color{black}ICML 2021}
\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint}
\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint}
\item \textbf{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.com/citations?user=ldJpvE8AAAAJ}{\color{linkcolour}Anastasia Koloskova}, \href{https://people.epfl.ch/martin.jaggi}{\color{linkcolour}Martin Jaggi}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{http://proceedings.mlr.press/v130/kovalev21a}{\em \color{black}AISTATS 2021}
\item \textbf{Linearly Converging Error Compensated SGD} (\href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{}{\color{linkcolour}Dmitry Makarenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{\em \color{black}NeurIPS 2020}
\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint}
\item \textbf{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{\em \color{black}NeurIPS 2020}
\item \textbf{From Local SGD to Local Fixed Point Methods for Federated Learning} (\href{https://scholar.google.com/citations?user=4w2W9KQAAAAJ}{\color{linkcolour}Grigory Malinovsky}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/malinovskiy20a.html}{\em \color{black}ICML 2020}
\item \textbf{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} (\href{https://zhizeli.github.io}{\color{linkcolour}Zhize Li}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://qianxunk.github.io}{\color{linkcolour}Xun Qian}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/li20g.html}{\em \color{black}ICML 2020}
\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M. Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint}
\item \textbf{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} (\href{https://fhanzely.github.io/index.html}{\color{linkcolour}Filip Hanzely}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/hanzely20b.html}{\em \color{black}ICML 2020}
\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint}
\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint}
\item \textbf{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://sites.google.com/site/optneurips19/}{\em \color{black}NeurIPS 2019 Workshop}
\item \textbf{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{\em \color{black}NeurIPS 2019}
\item \textbf{Revisiting Stochastic Extragradient} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=GI_-KjoAAAAJ}{\color{linkcolour}Yura Malitsky}), \href{http://proceedings.mlr.press/v108/mishchenko20a}{\em \color{black}AISTATS 2020}
\item \textbf{RSN: Randomized Subspace Newton} (\href{https://gowerrobert.github.io}{\color{linkcolour}Robert M. Gower}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://www.opt.uni-duesseldorf.de/~lieder/de/inhalt.php}{\color{linkcolour}Felix Lieder}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{\em \color{black}NeurIPS 2019}
\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U. Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint}
\item \textbf{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v117/kovalev20a}{\em \color{black}ALT 2020}
\item \textbf{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization} (\href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{http://crm-en.ics.org.ru/journal/article/2685/}{\em \color{black}Computer Research and Modeling}
\item \textbf{Stochastic Spectral and Conjugate Descent Methods} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{\em \color{black}NeurIPS 2018}
\end{enumerate}

### 2022-03-20 papers.py

@@ -8,6 +8,8 @@ import lxml.html
 import lxml.html.builder
 import json
 
+from unidecode import unidecode
+
 author_list = json.load(open('authors.json'))
 
 
@@ -57,8 +59,38 @@ for root, dirs, files in os.walk("papers"):
 
 paper_list.sort(key=lambda p: p._date, reverse=True)
 
-print('Papers:')
+
+# conference_list = {
+#     'NeurIPS 2021': 'huj',
+#     'NeurIPS 2020': 'huj',
+#     'NeurIPS 2019': 'huj',
+#     'NeurIPS 2018': 'huj',
+#     'ICML 2021': 'huj',
+#     'ICML 2020': 'huj',
+#     'AISTATS 2021': 'huj'}
+
+def convert_venue(title):
+    venue_list = {'arXiv': 'arXiv preprint',
+                  'CRM': 'Computer Research and Modeling'}
+    if title in venue_list.keys():
+        return venue_list[title]
+    return title
+
+
+file = open("CV2/papers.tex", "w")
+
+file.write('\\begin{enumerate}\n')
 for paper in paper_list:
-    print(paper.title)
+    file.write('\\item \\textbf{{{}}}'.format(paper.title))
+    file.write(' (')
     for author in paper.authors:
-        print('\t', author.title, author.href)
+        file.write('\\href{{{}}}{{\\color{{linkcolour}}{}}}'.format(
+            author.href, unidecode(author.title)))
+        if author != paper.authors[-1]:
+            file.write(', ')
+    file.write('), ')
+    file.write('{}'.format('\\href{{{}}}{{\\em \\color{{black}}{}}}'.format(
+        paper.links[1].href, convert_venue(paper.links[1].title))))
+    file.write('\n')
+file.write('\\end{enumerate}\n')
+file.close()

### 2022-03-20 CV2/CV.tex
cv

@@
 \section{Research Interests}
- Optimization Algorithms, Distributed Optimization, Machine Learning,
+Optimization Algorithms, Distributed Optimization, Machine Learning
+%\begin{tabular}{cl}
+%\qquad\qquad\qquad&  Optimization Algorithms\\
+%&  Distributed Optimization\\
+%&  Machine Learning
+%\end{tabular}
 
@@
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET\\
+	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
 	\textsc{Computer} & macOS, LaTeX, Git\\
@@
 	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
+	\textsc{2018} & {\bf Dean's Award}, King Abdullah University of Science and Technology\\
 	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
@@
 
-\section{Papers}
-
 \input{papers.tex}

### 2022-03-20 CV2/papers.tex
cv

@@
+\section{{Publications}}
 \begin{enumerate}
-\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint}
-\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint}
-\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint}
 \item \textbf{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{\em \color{black}NeurIPS 2021}
-\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint}
 \item \textbf{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{http://proceedings.mlr.press/v139/kovalev21a}{\em \color{black}ICML 2021}
-\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint}
-\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint}
 \item \textbf{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.com/citations?user=ldJpvE8AAAAJ}{\color{linkcolour}Anastasia Koloskova}, \href{https://people.epfl.ch/martin.jaggi}{\color{linkcolour}Martin Jaggi}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
@@
 \item \textbf{Linearly Converging Error Compensated SGD} (\href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{}{\color{linkcolour}Dmitry Makarenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{\em \color{black}NeurIPS 2020}
-\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint}
 \item \textbf{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{\em \color{black}NeurIPS 2020}
@@
 \item \textbf{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} (\href{https://zhizeli.github.io}{\color{linkcolour}Zhize Li}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://qianxunk.github.io}{\color{linkcolour}Xun Qian}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/li20g.html}{\em \color{black}ICML 2020}
-\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M.
-Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint}
 \item \textbf{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} (\href{https://fhanzely.github.io/index.html}{\color{linkcolour}Filip Hanzely}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/hanzely20b.html}{\em \color{black}ICML 2020}
-\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint}
-\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint}
 \item \textbf{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://sites.google.com/site/optneurips19/}{\em \color{black}NeurIPS 2019 Workshop}
@@
 Gower}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://www.opt.uni-duesseldorf.de/~lieder/de/inhalt.php}{\color{linkcolour}Felix Lieder}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{\em \color{black}NeurIPS 2019}
-\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
-Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint}
 \item \textbf{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v117/kovalev20a}{\em \color{black}ALT 2020}
@@
 \end{enumerate}
+\newpage
+\section{{Preprints}}
+\begin{enumerate}
+\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint (February 2022)}
+\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint (December 2021)}
+\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint (July 2021)}
+\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint (February 2021)}
+\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint (February 2021)}
+\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
+\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint (September 2020)}
+\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M.
+Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint (February 2020)}
+\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint (December 2019)}
+\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint (December 2019)}
+\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
+Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint (April 2019)}
+\end{enumerate}
+\bigskip
+\begin{center}
+Last Updated on March 20, 2022
+\end{center}

### 2022-03-20 papers.py

@@ -28,7 +28,7 @@ class Paper:
         self._id = id
         self._date = dateparser.parse(meta['date'][0])
 
-        self.date = self._date.strftime("%d %b %Y")
+        self.date = self._date.strftime("%B %Y")
 
         self.title = meta['title'][0]
 
@@ -70,8 +70,7 @@ paper_list.sort(key=lambda p: p._date, reverse=True)
 #     'AISTATS 2021': 'huj'}
 
 def convert_venue(title):
-    venue_list = {'arXiv': 'arXiv preprint',
-                  'CRM': 'Computer Research and Modeling'}
+    venue_list = {'CRM': 'Computer Research and Modeling'}
     if title in venue_list.keys():
         return venue_list[title]
     return title
@@ -79,8 +78,15 @@ def convert_venue(title):
 
 file = open("CV2/papers.tex", "w")
 
+# ------------------
+# WRITE PUBLICATIONS
+# ------------------
+
+file.write("\\section{{Publications}}\n")
 file.write('\\begin{enumerate}\n')
 for paper in paper_list:
+    if paper.links[1].title == 'arXiv':
+        continue
     file.write('\\item \\textbf{{{}}}'.format(paper.title))
     file.write(' (')
     for author in paper.authors:
@@ -93,4 +99,33 @@ for paper in paper_list:
         paper.links[1].href, convert_venue(paper.links[1].title))))
     file.write('\n')
 file.write('\\end{enumerate}\n')
+
+
+# ---------------
+# WRITE PREPRINTS
+# ---------------
+file.write("\\newpage\n")
+file.write("\\section{{Preprints}}\n")
+file.write('\\begin{enumerate}\n')
+for paper in paper_list:
+    if paper.links[1].title != 'arXiv':
+        continue
+    file.write('\\item \\textbf{{{}}}'.format(paper.title))
+    file.write(' (')
+    for author in paper.authors:
+        file.write('\\href{{{}}}{{\\color{{linkcolour}}{}}}'.format(
+            author.href, unidecode(author.title)))
+        if author != paper.authors[-1]:
+            file.write(', ')
+    file.write('), ')
+    file.write('\\href{{{}}}{{\\em \\color{{black}}{} ({})}}'.format(
+        paper.links[1].href, 'arXiv preprint', paper.date))
+    file.write('\n')
+file.write('\\end{enumerate}\n')
+
+file.write('\\bigskip\n')
[…]

### 2022-03-20 papers.py
-

@@ -104,7 +104,7 @@ file.write('\\end{enumerate}\n')
 # ---------------
 # WRITE PREPRINTS
 # ---------------
-file.write("\\newpage\n")
+# file.write("\\newpage\n")
 file.write("\\section{{Preprints}}\n")
 file.write('\\begin{enumerate}\n')
 for paper in paper_list:

### 2022-03-21 CV2/papers.tex
-
papers update

@@
 \item \textbf{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{\em \color{black}NeurIPS 2021}
+\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://aistats.org/aistats2022/accepted.html}{\em \color{black}AISTATS 2022}
 \item \textbf{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{http://proceedings.mlr.press/v139/kovalev21a}{\em \color{black}ICML 2021}
+\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=pFyXqxChZc}{\em \color{black}ICLR 2022}
 \item \textbf{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.com/citations?user=ldJpvE8AAAAJ}{\color{linkcolour}Anastasia Koloskova}, \href{https://people.epfl.ch/martin.jaggi}{\color{linkcolour}Martin Jaggi}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
@@
 \end{enumerate}
-\newpage
 \section{{Preprints}}
@@
 \item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint (July 2021)}
-\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.11079}{\em \color{black}arXiv preprint (February 2021)}
-\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2102.08374}{\em \color{black}arXiv preprint (February 2021)}
 \item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
@@
 \begin{center}
-Last Updated on March 20, 2022
+Last Updated on March 21, 2022
 \end{center}

### 2022-03-23 CV2/CV.tex
-

--- 2022-03-20 CV2/CV.tex
@@
 
-\section{Personal Data}
-
-\begin{tabular}{rl}
-\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
-\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
-\textsc{Phone} & +7 905 719 06 98\\
-\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
-\end{tabular}
-
-%----------------------------------------------------------------------------------------
-%	EDUCATION
-%----------------------------------------------------------------------------------------
-
-\section{Education}
-\begin{tabular}{rl}	
-\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
-& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
-& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-\textsc{2018-2019}& MS in Computer Science\\
-& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
-& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
-& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
-& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-\textsc{2019-Now}& PhD in Computer Science\\
-& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
-& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-\end{tabular}
-
-\section{Research Interests}
- Optimization Algorithms, Distributed Optimization, Machine Learning,
-
-\section{Skills}
-
-\begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET\\
-	\textsc{Computer} & macOS, LaTeX, Git\\
-	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
-\end{tabular}
-
-%----------------------------------------------------------------------------------------
-%	LANGUAGES
-%----------------------------------------------------------------------------------------
-\section{Languages}
-
-\begin{tabular}{rl}
-\textsc{English} & Advanced Knowledge \\
-\textsc{Russian} & Mothertongue\\
-\end{tabular}
-
-\section{Awards}
-\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
-\begin{tabular}{cl}
-	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
-	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
-	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
-	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
-	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
-	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
-	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
-	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
-	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
-	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
-	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
-	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
-	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
-\end{tabular}
-\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
-
-\newpage
-
-\section{Papers}
+\input{general}
 
@@
 
+\input{date.tex}
+
 \end{document}

### 2022-03-23 CV2/general.tex
-

\section{Personal Data}

\begin{tabular}{rl}
	\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
	\textsc{Phone} & +7 905 719 06 98\\
	\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
\end{tabular}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabular}{rl}	
	\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
	& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
	\textsc{2018-2019}& MS in Computer Science\\
	& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
	& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
	\textsc{2019-Now}& PhD in Computer Science\\
	& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\end{tabular}

\section{Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{tabularx}{\textwidth}{cX}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
	\textsc{2021} & {\bf PhD progress marked as Outstanding}, King Abdullah University of Science and Technology\\
	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
	\textsc{2018} & {\bf Dean's Award}, King Abdullah University of Science and Technology\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabularx}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	\qquad\qquad&  Optimization Algorithms\\
	&  Distributed Optimization\\
	&  Machine Learning
\end{tabular}

\section{Skills}

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}

\begin{tabular}{rl}
	\textsc{English} & Advanced Knowledge \\
	\textsc{Russian} & Mothertongue\\
\end{tabular}

### 2022-03-23 CV.py

@@ -122,8 +122,9 @@ for paper in paper_list:
         paper.links[1].href, 'arXiv preprint', paper.date))
     file.write('\n')
 file.write('\\end{enumerate}\n')
+file.close()
 
-file.write('\\bigskip\n')
+file = open("CV2/date.tex", "w")
 file.write('\\begin{center}\n')
 file.write('Last Updated on {}\n'.format(
     datetime.datetime.now().strftime('%B %d, %Y')))

### 2022-03-23 CV2/awards.tex
work on cv

\section{Honors and Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{enumerate}
	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)

	\item \textbf{Russian President’s Scholarship for High School Sudents}, given for prize-winning at final round of All-Russian School Olympiads, 2012-2014
	\item \textbf{Moscow Governor’s Scholarship for High School Sudents}, given for prize-winning at region and final rounds of All-Russian School Olympiads, 2012-2014

	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg, 2014
	\item \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow, 2014
	\item \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow, 2014

	\item \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok, 2013
	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk, 2012
\end{enumerate}
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

### 2022-03-23 CV2/general.tex
work on cv

@@
 
-\section{Awards}
-\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
-\begin{tabularx}{\textwidth}{cX}
-	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
-	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
-	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
-	\textsc{2021} & {\bf PhD progress marked as Outstanding}, King Abdullah University of Science and Technology\\
-	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
-	\textsc{2018} & {\bf Dean's Award}, King Abdullah University of Science and Technology\\
-	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
-	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
-	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
-	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
-	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
-	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
-	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
-	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
-	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
-\end{tabularx}
-\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
-
 \section{Research Interests}

### 2022-03-23 CV2/talks.tex
work on cv

\section{Conferences and Talks}
\begin{enumerate}
\item {\bf Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Saudi Arabia (June 2018)
\item {\bf Stochastic Spectral Descent Methods}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Rusia (February 2018)
\end{enumerate}

### 2022-03-23 CV.py

@@ -44,6 +44,34 @@ class Paper:
             else:
                 self.authors.append(Link(a, ''))
 
+
+class Talk:
+    def __init__(self, id, content):
+        md = markdown.Markdown(extensions=['meta'])
+        md.convert(content)
+        meta = md.Meta
+
+        self._id = id
+        self._date = dateparser.parse(meta['date'][0])
+
+        self.date = self._date.strftime("%B %Y")
+
+        self.title = meta['title'][0]
+        self.venue = meta['venue'][0]
+        self.location = meta['location'][0]
+
+        # links = json.loads(meta['links'][0])
+        # self.links = []
+        # for key in links:
+        #     self.links.append(Link(key, links[key]))
+
+        # self.authors = []
+        # for a in meta['authors']:
+        #     if a in author_list:
+        #         self.authors.append(Link(a, author_list[a]))
+        #     else:
+        #         self.authors.append(Link(a, ''))
+
 # -----------
 # LOAD PAPERS
 # -----------
@@ -58,6 +86,20 @@ for root, dirs, files in os.walk("papers"):
     break
 
 paper_list.sort(key=lambda p: p._date, reverse=True)
+
+
+# ----------
+# LOAD TALKS
+# ----------
+talk_list = []
+
+for root, dirs, files in os.walk("talks"):
+    for name in dirs:
+        input = open(os.path.join(root, name, "index.md"), "r")
+        talk_list.append(Talk(name, input.read()))
+    break
+
+talk_list.sort(key=lambda t: t._date, reverse=True)
 
 
 # conference_list = {
@@ -77,12 +119,10 @@ def convert_venue(title):
 
 
 file = open("CV2/papers.tex", "w")
-
 # ------------------
 # WRITE PUBLICATIONS
 # ------------------
-
-file.write("\\section{{Publications}}\n")
+file.write("\\section{Publications}\n")
 file.write('\\begin{enumerate}\n')
 for paper in paper_list:
     if paper.links[1].title == 'arXiv':
@@ -104,8 +144,7 @@ file.write('\\end{enumerate}\n')
 # ---------------
 # WRITE PREPRINTS
 # ---------------
-# file.write("\\newpage\n")
-file.write("\\section{{Preprints}}\n")
+file.write("\\section{Preprints}\n")
 file.write('\\begin{enumerate}\n')
 for paper in paper_list:
[…]

### 2022-03-23 CV2/talks.tex
talks

@@
 \begin{enumerate}
-\item {\bf Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Saudi Arabia (June 2018)
-\item {\bf Stochastic Spectral Descent Methods}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Rusia (February 2018)
+\item {\bf Talk: Revisiting Stochastic Extragradient Method}, {\em International Conference on Continuous Optimization 2019}, Technical University, Berlin, Germany (August 2019)
+\item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Data Science Summer School 2019}, Ecole Polytechnique, Paris, France (June 2019)
+\item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
+\item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Weekly Seminar <<Automatic control and Optimization Theory>>}, Institute for Control Problems, Moscow, Russia (March 2019)
+\item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Seminar <<Modern Optimization Methods>>}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
+\item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (June 2018)
+\item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (February 2018)
 \end{enumerate}

### 2022-03-23 CV2/talks.tex
-

@@
-\section{Conferences and Talks}
+\section{Conference Posters and Talks}
 \begin{enumerate}
+\item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em NeurIPS 2021}, Online (December 2021)
+\item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021}, Online (July 2021)
+\item {\bf Talk/Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em ICML 2021}, Online (July 2021)
+\item {\bf Talk/Poster: A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!}, {\em AISTATS 2021}, Online (April 2021)
+\item {\bf Poster: Linearly Converging Error Compensated SGD}, {\em NeurIPS 2020}, Online (December 2020)
+\item {\bf Talk/Poster: Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization}, {\em NeurIPS 2020}, Online (December 2020)
+\item {\bf Talk: Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems}, {\em ICML 2020}, Online (July 2020)
+\item {\bf Poster: RSN: Randomized Subspace Newton}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
+\item {\bf Poster: Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates}, {\em NeurIPS 2019}, Vancouver, Canada (December 2019)
 \item {\bf Talk: Revisiting Stochastic Extragradient Method}, {\em International Conference on Continuous Optimization 2019}, Technical University, Berlin, Germany (August 2019)
@@
 \item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Seminar <<Modern Optimization Methods>>}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
+\item {\bf Poster: Stochastic Spectral Descent Methods}, {\em NeurIPS 2018}, Montreal, Canada (December 2018)
 \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (June 2018)

### 2022-03-23 CV.py

@@ -179,7 +179,7 @@ file.close()
 # WRITE TALKS
 # -----------
 file = open("CV2/talks.tex", "w")
-file.write('\\section{Conferences and Talks}\n')
+file.write('\\section{Conference Posters and Talks}\n')
 file.write('\\begin{enumerate}\n')
 for talk in talk_list:
     file.write('\\item {{\\bf {}}}, {{\\em {}}}, {} ({})\n'.format(

### 2022-03-24 CV2/talks.tex
-

@@
 \begin{enumerate}
+\item {\bf Talk: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em Rising Stars in AI Symposium 2022}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (March 2022)
 \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em NeurIPS 2021}, Online (December 2021)
 \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021}, Online (July 2021)
+\item {\bf Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em Conference <<Optimization Without Borders>>}, Sirius University, Sochi, Russia (July 2021)
 \item {\bf Talk/Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em ICML 2021}, Online (July 2021)

### 2022-03-24 CV2/teaching.tex
-

\section{Teaching Experience}

\newcommand{\teaching}[3]{{\bf #1}, #2 (#3)}

\begin{enumerate}
	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}

%	Mini-seminar for

	\item \teaching{Project Mentor at <<Modern Information, Optimization and Control Methods>> Student Educational Program}{Sirius University, Sochi, Russia}{July-August 2021}

	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}

%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)

\end{enumerate}

### 2022-03-27 CV2/teaching.tex
cv

@@
 \begin{enumerate}
-	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
-%	Mini-seminar for
+	\item \teaching{Mentor for a Research Project with MIPT student Ekaterina Borodich (online)}{Moscow Institute of Physics and Technology, Moscow, Russia}{March 2022}
+
+	\item \teaching{Mentor for 2 Research Projects with KAUST Students Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
@@
 
-	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
-
-%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)
+	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (done during his internship at KAUST, resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
 

### 2022-05-22 CV2/papers.tex
-
work on cv
papers

@@
-\section{{Publications}}
+\section{Publications}
 \begin{enumerate}
@@
 \end{enumerate}
-\section{{Preprints}}
+\section{Preprints}
 \begin{enumerate}
+\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.09647}{\em \color{black}arXiv preprint (May 2022)}
+\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.05653}{\em \color{black}arXiv preprint (May 2022)}
 \item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint (February 2022)}
@@
 \end{enumerate}
-\bigskip
-\begin{center}
-Last Updated on March 21, 2022
-\end{center}

### 2022-06-29 CV2/papers.tex
papers

@@
 \begin{enumerate}
+\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{\em \color{black}OPTIMA 2021}
 \item \textbf{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{\em \color{black}NeurIPS 2021}
@@
 \begin{enumerate}
+\item \textbf{On Scaled Methods for Saddle Point Problems} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{}{\color{linkcolour}Aibek Alanov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2206.08303}{\em \color{black}arXiv preprint (June 2022)}
+\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2206.00090}{\em \color{black}arXiv preprint (May 2022)}
+\item \textbf{Decentralized Computation of Wasserstein Barycenter over Time-Varying Networks} (\href{https://scholar.google.com/citations?user=v6tuw7IAAAAJ}{\color{linkcolour}Olga Yufereva}, \href{}{\color{linkcolour}Michael Persiianov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2205.15669}{\em \color{black}arXiv preprint (May 2022)}
+\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://arxiv.org/abs/2205.15136}{\em \color{black}arXiv preprint (May 2022)}
 \item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.09647}{\em \color{black}arXiv preprint (May 2022)}
@@
 \item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint (December 2021)}
-\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2107.05957}{\em \color{black}arXiv preprint (July 2021)}
 \item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}

### 2022-10-30 CV2/papers.tex
NeurIPS 2022 papers

@@
 \begin{enumerate}
+\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=52846}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=55134}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53388}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53395}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=55123}{\em \color{black}NeurIPS 2022}
+\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53383}{\em \color{black}NeurIPS 2022}
 \item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{\em \color{black}OPTIMA 2021}
@@
 Gower}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://www.opt.uni-duesseldorf.de/~lieder/de/inhalt.php}{\color{linkcolour}Felix Lieder}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{\em \color{black}NeurIPS 2019}
+\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
+Stich}), \href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{\em \color{black}Optimization Methods and Software}
 \item \textbf{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v117/kovalev20a}{\em \color{black}ALT 2020}
@@
 \item \textbf{Decentralized Computation of Wasserstein Barycenter over Time-Varying Networks} (\href{https://scholar.google.com/citations?user=v6tuw7IAAAAJ}{\color{linkcolour}Olga Yufereva}, \href{}{\color{linkcolour}Michael Persiianov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2205.15669}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://arxiv.org/abs/2205.15136}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.09647}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2205.05653}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2202.02771}{\em \color{black}arXiv preprint (February 2022)}
-\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://arxiv.org/abs/2112.15199}{\em \color{black}arXiv preprint (December 2021)}
 \item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
@@
 \item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint (December 2019)}
-\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
-Stich}), \href{https://arxiv.org/abs/1904.05115}{\em \color{black}arXiv preprint (April 2019)}
 \end{enumerate}

### 2022-10-30 CV2/general.tex
new papers

@@
 	&  Distributed Optimization\\
+	& Federated Learning\\
 	&  Machine Learning
@@
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
+	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures\\& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
+	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
 	\textsc{Computer} & macOS, LaTeX, Git\\
-	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
 \end{tabular}

### 2022-10-30 CV2/papers.tex
new papers

@@
 \begin{enumerate}
+\item \textbf{Accelerated Variance-Reduced Methods for Saddle-Point Problems} (\href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{}{\color{linkcolour}Vladislav Tominin}, \href{}{\color{linkcolour}Yaroslav Tominin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}), \href{https://www.sciencedirect.com/science/article/pii/S2192440622000247}{\em \color{black}EURO Journal on Computational Optimization}
 \item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=52846}{\em \color{black}NeurIPS 2022}
@@
 \item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=pFyXqxChZc}{\em \color{black}ICLR 2022}
+\item \textbf{Accelerated Methods for Saddle-Point Problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}), \href{https://link.springer.com/article/10.1134/S0965542520110020}{\em \color{black}Computational Mathematics and Mathematical Physics}
 \item \textbf{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.com/citations?user=ldJpvE8AAAAJ}{\color{linkcolour}Anastasia Koloskova}, \href{https://people.epfl.ch/martin.jaggi}{\color{linkcolour}Martin Jaggi}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
@@
 \item \textbf{Linearly Converging Error Compensated SGD} (\href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{}{\color{linkcolour}Dmitry Makarenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{\em \color{black}NeurIPS 2020}
+\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{\em \color{black}OPTIMA 2021}
 \item \textbf{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{\em \color{black}NeurIPS 2020}
@@
 Gower}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://www.opt.uni-duesseldorf.de/~lieder/de/inhalt.php}{\color{linkcolour}Felix Lieder}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{\em \color{black}NeurIPS 2019}
-\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
+\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Double Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
 Stich}), \href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{\em \color{black}Optimization Methods and Software}
@@
 \begin{enumerate}
+\item \textbf{Decentralized Optimization over Time-varying Graphs: a Survey} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{}{\color{linkcolour}Aleksander Beznosikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2210.09719}{\em \color{black}arXiv preprint (October 2022)}
+\item \textbf{Smooth Monotone Stochastic Variational Inequalities and Saddle Point Problems - Survey} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://sites.google.com/site/lab7polyak/}{\color{linkcolour}Boris Polyak}, \href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2208.13592}{\em \color{black}arXiv preprint (August 2022)}
 \item \textbf{On Scaled Methods for Saddle Point Problems} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{}{\color{linkcolour}Aibek Alanov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2206.08303}{\em \color{black}arXiv preprint (June 2022)}
@@
 \item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
-\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://arxiv.org/abs/2009.11069}{\em \color{black}arXiv preprint (September 2020)}
 \item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M.

### 2022-10-30 CV2/general.tex
website, bio, address, CV, etc.

@@
 	\textsc{Phone} & +7 905 719 06 98\\
-	\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
+	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
+	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}
 \end{tabular}
@@
 	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-	\textsc{2019-Now}& PhD in Computer Science\\
+	\textsc{2019-2022}& PhD in Computer Science\\
 	& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
@@
 \begin{tabular}{cl}
-	\qquad\qquad&  Optimization Algorithms\\
-	&  Distributed Optimization\\
-	& Federated Learning\\
+	\qquad\qquad&  Optimization\\
+	& Federated and Distributed Learning\\
 	&  Machine Learning

### 2022-10-31 CV2/general.tex
-

@@
 	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
-	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}
+	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
+	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}
+\end{tabular}
+
+%----------------------------------------------------------------------------------------
+%	POSITIONS
+%----------------------------------------------------------------------------------------
+
+\section{Positions}
+\begin{tabular}{rl}	
+	\textsc{2022-Now}& Postdoctoral Researcher\\
+	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
 \end{tabular}
@@
 \begin{tabular}{rl}	
-	\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
-	& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
+	\textsc{2019-2022}& PhD in Computer Science\\
+	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
+	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
+	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
+	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
 	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
 	\textsc{2018-2019}& MS in Computer Science\\
-	& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
+	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
 	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
-	& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
+	\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
+	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
 	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-	\textsc{2019-2022}& PhD in Computer Science\\
-	& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
-	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
 \end{tabular}

### 2022-10-31 CV2/general.tex
-

@@
 	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
+	\textsc{2022}& Researcher\\
+	&Laboratory of Advanced Combinatorics and Network Applications\\
+	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
+	\textsc{2021-2022}& Research Intern\\
+	 &Research Center for Trusted Artificial Intelligence\\
+	 &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia
 \end{tabular}
@@
 \begin{tabular}{cl}
-	\qquad\qquad&  Optimization\\
+	&  Optimization\\
 	& Federated and Distributed Learning\\
@@
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures\\& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia\\
+	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, Jax, Pytorch\\
+	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, HTML/CSS\\
 	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\

### 2022-10-31 CV2/teaching.tex
-

--- 2022-03-24 CV2/teaching.tex
@@
 \begin{enumerate}
-	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
-%	Mini-seminar for
+	\item \teaching{Mentor for a Research Project with MIPT student Ekaterina Borodich (online, led to NeurIPS 2022 paper <<Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity>>)}{Moscow Institute of Physics and Technology, Moscow, Russia}{March 2022}
+
+	\item \teaching{Mentor for a Research Project with KAUST Student Abdurakhmon Sadiev (led to NeurIPS 2022 paper <<Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
@@
 
-	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
-
-%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)
+	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (done during his internship at KAUST, led to ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
 

### 2022-10-31 CV2/general.tex
mobile and email
CV thesis summary

@@
 	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
-	\textsc{Phone} & +7 905 719 06 98\\
+	\textsc{Phone} &  +32 499 34 93 21 (Belgium)\\
+	\textsc{Phone} & +7 905 719 06 98 (Russia)\\
 	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
@@
 	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}
+
 \end{tabular}
@@
 	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
+	& Thesis: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
+	& \hspace{\widthof{Thesis: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
+	& Defense Committee: -- External: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Yurii Nesterov}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Arkadi Nemirovsky}\\
+	&\hspace{\widthof{Defense Committee: }}-- Internal: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E.
+Keyes}, \href{https://shao3wangdi.github.io}{Di Wang}, \href{https://scholar.google.com/citations?user=Vj2D8JQAAAAJ}{Matteo Parsani}\\
 	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\

### 2022-10-31 CV2/teaching.tex
CV thesis summary

--- 2022-03-24 CV2/teaching.tex
@@
 \begin{enumerate}
-	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
-%	Mini-seminar for
+	\item \teaching{Mentor for a Research Project with MIPT student Ekaterina Borodich (online, led to NeurIPS 2022 paper ``Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity'')}{Moscow Institute of Physics and Technology, Moscow, Russia}{March 2022}
+
+	\item \teaching{Mentor for a Research Project with KAUST Student Abdurakhmon Sadiev (led to NeurIPS 2022 paper ``Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox'')}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}
 
@@
 
-	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
-
-%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)
+	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (done during his internship at KAUST, led to ICML 2020 paper ``From Local SGD to Local Fixed Point Methods for Federated Learning'')}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
 

### 2022-11-01 CV2/general.tex
-

@@
 	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, Jax, Pytorch\\
-	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, HTML/CSS\\
+	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
 	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
 	\textsc{Computer} & macOS, LaTeX, Git\\
+	\textsc{Languages} & English (Advanced), Russian (Native)
 \end{tabular}

### 2022-11-01 CV2/general.tex
-

--- 2022-10-31 CV2/general.tex
@@
 \begin{tabular}{cl}
-	&  Optimization\\
-	& Federated and Distributed Learning\\
-	&  Machine Learning
+	&  Optimization, Federated and Distributed Learning\\
+	&Machine Learning, Deep Learning
 \end{tabular}
@@
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, Jax, Pytorch\\
-	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, HTML/CSS\\
+	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, JAX, PyTorch\\
+	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
 	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
 	\textsc{Computer} & macOS, LaTeX, Git\\
+%	\textsc{Languages} & English (Advanced), Russian (Native)
 \end{tabular}

### 2022-11-02 CV2/papers.tex
neurips 2022 openreview

@@
 \item \textbf{Accelerated Variance-Reduced Methods for Saddle-Point Problems} (\href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{}{\color{linkcolour}Vladislav Tominin}, \href{}{\color{linkcolour}Yaroslav Tominin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}), \href{https://www.sciencedirect.com/science/article/pii/S2192440622000247}{\em \color{black}EURO Journal on Computational Optimization}
-\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=52846}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=55134}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53388}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53395}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=55123}{\em \color{black}NeurIPS 2022}
-\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://nips.cc/Conferences/2022/Schedule?showEvent=53383}{\em \color{black}NeurIPS 2022}
+\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=W72rB0wwLVu}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://openreview.net/forum?id=QrK0WDLVHZt}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=YgmiL2Ur01P}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=pD5Pl5hen_g}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=omI5hgwgrsa}{\em \color{black}NeurIPS 2022}
+\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=FncDhRcRYiN}{\em \color{black}NeurIPS 2022}
 \item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{\em \color{black}OPTIMA 2021}

### 2023-07-17 CV2/general.tex
-

@@
 	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
-	\textsc{2022}& Researcher\\
+	\textsc{2022-2023}& Researcher\\
 	&Laboratory of Advanced Combinatorics and Network Applications\\
 	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
-	\textsc{2021-2022}& Research Intern\\
+	\textsc{2021-2023}& Research Intern\\
 	 &Research Center for Trusted Artificial Intelligence\\
@@
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, JAX, PyTorch\\
-	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
+	\textsc{Programming} & C/C++, Python,
+	Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}), JAX,\\
+	&PyTorch; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
 	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
 	\textsc{Computer} & macOS, LaTeX, Git\\
+		\textsc{Languages} & English (Advanced), Russian (Native)
+\end{tabular}
+
+%\begin{tabular}{rl}
+%	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}),\\
+%	& JAX, PyTorch\\
+%	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
+%	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
+%	\textsc{Computer} & macOS, LaTeX, Git\\
 %	\textsc{Languages} & English (Advanced), Russian (Native)
-\end{tabular}
+%\end{tabular}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Languages}
-
-\begin{tabular}{rl}
-	\textsc{English} & Advanced Knowledge \\
-	\textsc{Russian} & Mothertongue\\
-\end{tabular}
+%\section{Languages}
+%
+%\begin{tabular}{rl}
+%	\textsc{English} & Advanced Knowledge \\
+%	\textsc{Russian} & Mothertongue\\
+%\end{tabular}

### 2023-08-07 CV2/papers.tex
-

@@
 \begin{enumerate}
+\item \textbf{Is Consensus Acceleration Possible in Decentralized Optimization over Slowly Time-Varying Networks?} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=DwDQNKF4oy}{\em \color{black}ICML 2023}
 \item \textbf{Accelerated Variance-Reduced Methods for Saddle-Point Problems} (\href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{}{\color{linkcolour}Vladislav Tominin}, \href{}{\color{linkcolour}Yaroslav Tominin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}), \href{https://www.sciencedirect.com/science/article/pii/S2192440622000247}{\em \color{black}EURO Journal on Computational Optimization}
-\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=W72rB0wwLVu}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://openreview.net/forum?id=QrK0WDLVHZt}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=YgmiL2Ur01P}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=pD5Pl5hen_g}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=omI5hgwgrsa}{\em \color{black}NeurIPS 2022}
-\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=FncDhRcRYiN}{\em \color{black}NeurIPS 2022}
+\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/88c3c482430a62d35e03926a22e4b67e-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/d88f6f81e1aaf606776ffdd06fdf24ef-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/e56f394bbd4f0ec81393d767caa5a31b-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/5e2ed801f62102f531d109d7c6e1b62f-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/c959bb2cb164d37569a17fa67494d69a-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/883f66687a521536c505f9b2fbdcbf1e-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
 \item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{\em \color{black}OPTIMA 2021}

### 2023-10-15 CV2/general.tex
CV

@@
 \begin{tabular}{rl}	
-	\textsc{2022-Now}& Postdoctoral Researcher\\
+	\textsc{2021-Now}& Research Intern\\
+	&Research Center for Trusted Artificial Intelligence\\
+	&\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia\\
+	\textsc{2022-2023}& Postdoctoral Researcher\\
 	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
@@
 	&Laboratory of Advanced Combinatorics and Network Applications\\
-	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
-	\textsc{2021-2023}& Research Intern\\
-	 &Research Center for Trusted Artificial Intelligence\\
-	 &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia
+	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia
 \end{tabular}

### 2023-11-15 CV2/general.tex
CV and papers

@@
 \begin{tabular}{rl}	
-	\textsc{2021-Now}& Research Intern\\
+	\textsc{2023-Now}& Senior Researcher\\
+	&\textbf{\href{https://research.yandex.com}{\color{black}Yandex Research}}, Moscow, Russia\\
+	\textsc{2021-2023}& Research Intern\\
 	&Research Center for Trusted Artificial Intelligence\\
@@
 	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
-	\textsc{2022-2023}& Researcher\\
+	\textsc{2022}& Researcher\\
 	&Laboratory of Advanced Combinatorics and Network Applications\\

### 2023-11-15 CV2/papers.tex
CV and papers

@@
 \begin{enumerate}
+\item \textbf{Non-smooth setting of stochastic decentralized convex optimization problem over time-varying graphs} (\href{}{\color{linkcolour}Aleksandr Lobanov}, \href{}{\color{linkcolour}Andrew Veprikov}, \href{}{\color{linkcolour}Georgiy Konin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://link.springer.com/article/10.1007/s10287-023-00479-7}{\em \color{black}Computational Management Science}
 \item \textbf{Is Consensus Acceleration Possible in Decentralized Optimization over Slowly Time-Varying Networks?} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=DwDQNKF4oy}{\em \color{black}ICML 2023}
@@
 \item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper_files/paper/2022/hash/88c3c482430a62d35e03926a22e4b67e-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
+\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://link.springer.com/article/10.1007/s10287-023-00485-9}{\em \color{black}Computational Management Science}
 \item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/d88f6f81e1aaf606776ffdd06fdf24ef-Abstract-Conference.html}{\em \color{black}NeurIPS 2022}
@@
 \item \textbf{On Scaled Methods for Saddle Point Problems} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{}{\color{linkcolour}Aibek Alanov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2206.08303}{\em \color{black}arXiv preprint (June 2022)}
-\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2206.00090}{\em \color{black}arXiv preprint (May 2022)}
 \item \textbf{Decentralized Computation of Wasserstein Barycenter over Time-Varying Networks} (\href{https://scholar.google.com/citations?user=v6tuw7IAAAAJ}{\color{linkcolour}Olga Yufereva}, \href{}{\color{linkcolour}Michael Persiianov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2205.15669}{\em \color{black}arXiv preprint (May 2022)}

### 2023-11-17 TEST/assets/js/highlight.js
TEST

@@ -1,0 +1,32 @@
+function updateClass(){
+    max_index = 0;
+    
+    $(".nav-link-section").each(function(index){
+        section = $($(this).attr("href"))
+        offset = section.offset().top - $(window).scrollTop() - parseInt($("body").css("margin-top"), 10);
+
+        if (offset <= 3 && max_index < index){
+            max_index = index;
+        }
+        
+    });
+    
+    if ($('.bottom').offset().top <= $(window).scrollTop() + (window.innerHeight || $(window).height())){
+        max_index = $('.nav-link-section').length - 1;
+    }
+    
+    $(".nav-link-section").each(function(index){
+        if(index == max_index){
+            $(this).addClass("active");
+        }else{
+            $(this).removeClass("active");
+        }
+    }); 
+}
+
+$(document).ready(function(){
+    updateClass();
+    $(document).scroll(function(){
+        updateClass();
+    });
+});

### 2023-11-17 TEST/assets/js/scroll.js

@@ -1,0 +1,46 @@
+function scroll(elem){
+    if (elem.length == 1){
+        var offset = elem.offset().top - parseInt($("body").css("margin-top"), 10);
+
+        $("html, body").stop();
+        $("html, body").animate({
+            scrollTop: offset
+        }, 800);
+    }
+}
+
+function process_hash(){
+    var hash = window.location.hash;
+    window.location.hash = "";
+    scroll($(hash));
+}
+
+
+
+$(document).ready(function(){
+    
+    process_hash();
+
+    $(window).on('hashchange',function(){ 
+        process_hash();
+    });
+    
+    $(".nav-link").click(function(event){
+        if ($(".navbar-toggler").css("display") != "none"){
+            $(".navbar-toggler").trigger("click");
+        }
+    });
+    
+    $("a").click(function(event){
+        var href = $(this).attr("href");
+        
+        if (href.length > 0 && href[0] == '#'){
+            var elem = $(href);
+            
+            if (elem.length == 1){
+                event.preventDefault();
+                scroll(elem);
+            }
+        }   
+    });
+});

### 2023-11-17 TEST/main.py

@@ -1,0 +1,78 @@
+import jinja2
+import os
+import markdown
+import dateparser
+import json
+import datetime
+import lxml.html
+import lxml.html.builder
+import json
+
+
+author_list = json.load(open('authors.json'))
+
+
+class Link:
+    def __init__(self, title, href):
+        self.title = title
+        self.href = href
+
+
+class Paper:
+    def __init__(self, id, content):
+        md = markdown.Markdown(extensions=['meta'])
+        md.convert(content)
+        meta = md.Meta
+
+        self._id = id
+        self._date = dateparser.parse(meta['date'][0])
+
+        self.date = self._date.strftime("%d %b %Y")
+
+        self.title = meta['title'][0]
+
+        links = json.loads(meta['links'][0])
+        self.links = []
+        for key in links:
+            self.links.append(Link(key, links[key]))
+
+        self.authors = []
+        for a in meta['authors']:
+            if a in author_list:
+                self.authors.append(Link(a, author_list[a]))
+            else:
+                self.authors.append(Link(a, ''))
+
+
+paper_list = []
+
+for root, dirs, files in os.walk("papers"):
+    for name in dirs:
+        input = open(os.path.join(root, name, "index.md"), "r")
+        paper_list.append(Paper(name, input.read()))
+    break
+
+paper_list.sort(key=lambda p: p._date, reverse=True)
+
+
+publication_list = []
+preprint_list = []
+
+for p in paper_list:
+    if p.links[1].title == 'arXiv':
+        preprint_list += [p]
+    else:
+        publication_list += [p]
+
+
+
+
+
+file_loader = jinja2.FileSystemLoader('')
+env = jinja2.Environment(loader=file_loader)
+template = env.get_template('template_index.html')
+
+output = template.render(publications=publication_list[:5],
+                         preprints=preprint_list[:5],
+                         year=str(datetime.datetime.now().year))
+open('index.html', 'w').write(output)

### 2023-11-17 TEST/main.py
-

@@ -72,7 +72,7 @@ file_loader = jinja2.FileSystemLoader('')
 env = jinja2.Environment(loader=file_loader)
 template = env.get_template('template_index.html')
 
-output = template.render(publications=publication_list[:5],
-                         preprints=preprint_list[:5],
+output = template.render(publications=publication_list,
+                         preprints=preprint_list,
                          year=str(datetime.datetime.now().year))
 open('index.html', 'w').write(output)

### 2023-11-18 assets/js/highlight.js
JS update

@@ -1,32 +1,33 @@
-function updateClass(){
+function updateClass() {
     max_index = 0;
-    
-    $(".nav-link-section").each(function(index){
+    contact_index = 0;
+
+    $(".nav-link-section").each(function (index) {
         section = $($(this).attr("href"))
         offset = section.offset().top - $(window).scrollTop() - parseInt($("body").css("margin-top"), 10);
 
-        if (offset <= 3 && max_index < index){
+        if (offset <= 3 && max_index < index) {
             max_index = index;
         }
-        
+
     });
-    
-    if ($('.bottom').offset().top <= $(window).scrollTop() + (window.innerHeight || $(window).height())){
+
+    if ($('.bottom').offset().top <= $(window).scrollTop() + (window.innerHeight || $(window).height())) {
         max_index = $('.nav-link-section').length - 1;
     }
-    
-    $(".nav-link-section").each(function(index){
-        if(index == max_index){
+
+    $(".nav-link-section").each(function (index) {
+        if (index == max_index) {
             $(this).addClass("active");
-        }else{
+        } else {
             $(this).removeClass("active");
         }
-    }); 
+    });
 }
 
-$(document).ready(function(){
+$(document).ready(function () {
     updateClass();
-    $(document).scroll(function(){
+    $(document).scroll(function () {
         updateClass();
     });
 });

### 2023-11-18 assets/js/hl.js

@@ -1,0 +1,34 @@
+function updateClass() {
+    max_index = 0
+    last_index = 0
+
+    $('.nav-link-section').each(function (index) {
+        offset = $(document).scrollTop() + $('body').cssNumber('margin-top') - $($(this).attr('href')).offset().top
+        if (offset >= 0 && max_index < index) {
+            max_index = index
+        }
+        if (last_index < index) {
+            last_index = index;
+        }
+    })
+
+    bottom_offset = $(document).scrollTop() + window.innerHeight - $('.bottom').offset().top
+    if (bottom_offset >= 0) {
+        max_index = last_index;
+    }
+
+    $('.nav-link-section').each(function (index) {
+        if (index == max_index) {
+            $(this).addClass("active");
+        } else {
+            $(this).removeClass("active");
+        }
+    });
+}
+
+$(document).ready(function () {
+    updateClass()
+    $(document).scroll(function () {
+        updateClass()
+    });
+});

### 2023-11-18 assets/js/sc.js

@@ -1,0 +1,19 @@
+function scroll(sec_id) {
+    console.log('scroll', sec_id);
+    element = $(sec_id)
+    if (element.length != 1) {
+        return
+    }
+    offset = element.offset().top - $('body').cssNumber('margin-top');
+    $('html, body').stop();
+    $('html, body').animate({
+        scrollTop: offset
+    }, 800);
+}
+
+$(document).ready(function () {
+    $('.nav-link').click(function (event) {
+        scroll($(this).attr('href'));
+        return false;
+    });
+})

### 2023-11-18 assets/js/hl.js
-

@@ -12,9 +12,12 @@ function updateClass() {
         }
     })
 
-    bottom_offset = $(document).scrollTop() + window.innerHeight - $('.bottom').offset().top
-    if (bottom_offset >= 0) {
-        max_index = last_index;
+    // bottom_offset = $(document).scrollTop() + window.innerHeight - $('.bottom').offset().top
+    // if (bottom_offset >= 0) {
+    //     max_index = last_index;
+    // }
+    if ($('.bottom').offset().top <= $(window).scrollTop() + (window.innerHeight || $(window).height())){
+        max_index = $('.nav-link-section').length - 1;
     }
 
     $('.nav-link-section').each(function (index) {

### 2023-11-18 assets/js/hl.js
-

@@ -4,7 +4,7 @@ function updateClass() {
 
     $('.nav-link-section').each(function (index) {
         offset = $(document).scrollTop() + $('body').cssNumber('margin-top') - $($(this).attr('href')).offset().top
-        if (offset >= 0 && max_index < index) {
+        if (offset >= -5 && max_index < index) {
             max_index = index
         }
         if (last_index < index) {
@@ -12,13 +12,11 @@ function updateClass() {
         }
     })
 
-    // bottom_offset = $(document).scrollTop() + window.innerHeight - $('.bottom').offset().top
-    // if (bottom_offset >= 0) {
-    //     max_index = last_index;
-    // }
-    if ($('.bottom').offset().top <= $(window).scrollTop() + (window.innerHeight || $(window).height())){
-        max_index = $('.nav-link-section').length - 1;
+    bottom_offset = $(document).scrollTop() + window.innerHeight - $('.bottom').offset().top
+    if (bottom_offset >= 0) {
+        max_index = last_index;
     }
+    
 
     $('.nav-link-section').each(function (index) {
         if (index == max_index) {

### 2023-11-18 assets/js/sc.js
-

@@ -14,6 +14,9 @@ function scroll(sec_id) {
 $(document).ready(function () {
     $('.nav-link').click(function (event) {
         scroll($(this).attr('href'));
+        if ($('.navbar-toggler').css('display') != 'none') {
+            $('.navbar-toggler').trigger('click');
+        }
         return false;
     });
 })

### 2024-08-13 CV2/papers.tex
CV

--- 2022-11-02 CV2/papers.tex
@@
 \begin{enumerate}
-\item \textbf{Accelerated Variance-Reduced Methods for Saddle-Point Problems} (\href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{}{\color{linkcolour}Vladislav Tominin}, \href{}{\color{linkcolour}Yaroslav Tominin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}), \href{https://www.sciencedirect.com/science/article/pii/S2192440622000247}{\em \color{black}EURO Journal on Computational Optimization}
-\item \textbf{Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox} (\href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=W72rB0wwLVu}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=9Dapoy8AAAAJ}{\color{linkcolour}Ekaterina Borodich}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://engineering.purdue.edu/~gscutari/}{\color{linkcolour}Gesualdo Scutari}), \href{https://openreview.net/forum?id=QrK0WDLVHZt}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Acceleration of High-Order Methods in Smooth Convex Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=YgmiL2Ur01P}{\em \color{black}NeurIPS 2022}
-\item \textbf{The First Optimal Algorithm for Smooth and Strongly-Convex-Strongly-Concave Minimax Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=pD5Pl5hen_g}{\em \color{black}NeurIPS 2022}
-\item \textbf{Optimal Algorithms for Decentralized Stochastic Variational Inequalities} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=R-xZRIAAAAAJ&hl=ru}{\color{linkcolour}Abdurakhmon Sadiev}, \href{}{\color{linkcolour}Michael Persiianov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://openreview.net/forum?id=omI5hgwgrsa}{\em \color{black}NeurIPS 2022}
-\item \textbf{Accelerated Primal-Dual Gradient Method for Smooth and Convex-Concave Saddle-Point Problems with Bilinear Coupling} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=FncDhRcRYiN}{\em \color{black}NeurIPS 2022}
-\item \textbf{Near-Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{\em \color{black}OPTIMA 2021}
-\item \textbf{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{\em \color{black}NeurIPS 2021}
-\item \textbf{An Optimal Algorithm for Strongly Convex Minimization under Affine Constraints} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://aistats.org/aistats2022/accepted.html}{\em \color{black}AISTATS 2022}
-\item \textbf{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{http://proceedings.mlr.press/v139/kovalev21a}{\em \color{black}ICML 2021}
-\item \textbf{IntSGD: Floatless Compression of Stochastic Gradients} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://bokunwang1.github.io}{\color{linkcolour}Bokun Wang}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://openreview.net/forum?id=pFyXqxChZc}{\em \color{black}ICLR 2022}
-\item \textbf{Accelerated Methods for Saddle-Point Problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}), \href{https://link.springer.com/article/10.1134/S0965542520110020}{\em \color{black}Computational Mathematics and Mathematical Physics}
-\item \textbf{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.com/citations?user=ldJpvE8AAAAJ}{\color{linkcolour}Anastasia Koloskova}, \href{https://people.epfl.ch/martin.jaggi}{\color{linkcolour}Martin Jaggi}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
-Stich}), \href{http://proceedings.mlr.press/v130/kovalev21a}{\em \color{black}AISTATS 2021}
-\item \textbf{Linearly Converging Error Compensated SGD} (\href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{}{\color{linkcolour}Dmitry Makarenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{\em \color{black}NeurIPS 2020}
-\item \textbf{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{}{\color{linkcolour}Vladislav Lukoshkin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}), \href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{\em \color{black}OPTIMA 2021}
-\item \textbf{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{\em \color{black}NeurIPS 2020}
-\item \textbf{From Local SGD to Local Fixed Point Methods for Federated Learning} (\href{https://scholar.google.com/citations?user=4w2W9KQAAAAJ}{\color{linkcolour}Grigory Malinovsky}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://lcondat.github.io}{\color{linkcolour}Laurent Condat}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/malinovskiy20a.html}{\em \color{black}ICML 2020}
-\item \textbf{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} (\href{https://zhizeli.github.io}{\color{linkcolour}Zhize Li}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://qianxunk.github.io}{\color{linkcolour}Xun Qian}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/li20g.html}{\em \color{black}ICML 2020}
-\item \textbf{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} (\href{https://fhanzely.github.io/index.html}{\color{linkcolour}Filip Hanzely}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v119/hanzely20b.html}{\em \color{black}ICML 2020}
-\item \textbf{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://sites.google.com/site/optneurips19/}{\em \color{black}NeurIPS 2019 Workshop}
-\item \textbf{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} (\href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{\em \color{black}NeurIPS 2019}
-\item \textbf{Revisiting Stochastic Extragradient} (\href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://shulgin-egor.github.io}{\color{linkcolour}Egor Shulgin}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=GI_-KjoAAAAJ}{\color{linkcolour}Yura Malitsky}), \href{http://proceedings.mlr.press/v108/mishchenko20a}{\em \color{black}AISTATS 2020}
-\item \textbf{RSN: Randomized Subspace Newton} (\href{https://gowerrobert.github.io}{\color{linkcolour}Robert M.
-Gower}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://www.opt.uni-duesseldorf.de/~lieder/de/inhalt.php}{\color{linkcolour}Felix Lieder}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{\em \color{black}NeurIPS 2019}
-\item \textbf{Stochastic Distributed Learning with Gradient Quantization and Double Variance Reduction} (\href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://konstmish.github.io}{\color{linkcolour}Konstantin Mishchenko}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://sstich.ch}{\color{linkcolour}Sebastian U.
-Stich}), \href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{\em \color{black}Optimization Methods and Software}
-\item \textbf{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://samuelhorvath.github.io}{\color{linkcolour}Samuel Horvath}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{http://proceedings.mlr.press/v117/kovalev20a}{\em \color{black}ALT 2020}
-\item \textbf{A hypothesis about the rate of global convergence for optimal methods (Newton's type) in smooth convex optimization} (\href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{http://crm-en.ics.org.ru/journal/article/2685/}{\em \color{black}Computer Research and Modeling}
-\item \textbf{Stochastic Spectral and Conjugate Descent Methods} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://elnurgasanov.com}{\color{linkcolour}Elnur Gasanov}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}), \href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{\em \color{black}NeurIPS 2018}
+\item
+\textbf{\href{https://link.springer.com/article/10.1007/s10287-023-00493-9}{Decentralized convex optimization on time-varying networks with application to Wasserstein barycenters}} (Olga Yufereva, Michael Persiianov, Pavel Dvurechensky, Alexander Gasnikov, Dmitry Kovalev).
+\textit{Computational Management Science}, 2024.
+\item
+\textbf{\href{https://link.springer.com/article/10.1007/s10287-023-00485-9}{Decentralized saddle-point problems with different constants of strong convexity and strong concavity}} (Dmitry Metelev, Alexander Rogozin, Alexander Gasnikov, Dmitry Kovalev).
+\textit{Computational Management Science}, 2024.
+\item
+\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2023.2280062}{Decentralized saddle point problems via non-Euclidean mirror prox}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
+\textit{Optimization Methods and Software}, 2024.
+\item
+\textbf{\href{https://link.springer.com/article/10.1007/s10287-023-00479-7}{Non-smooth setting of stochastic decentralized convex optimization problem over time-varying graphs}} (Aleksandr Lobanov, Andrew Veprikov, Georgiy Konin, Aleksandr Beznosikov, Alexander Gasnikov, Dmitry Kovalev).
+\textit{Computational Management Science}, 2023.
+\item
+\textbf{\href{https://link.springer.com/content/pdf/10.1007/978-3-030-54621-2_860-1.pdf}{Decentralized Convex Optimization over Time-Varying Graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev).
+\textit{Encyclopedia of Optimization}, 2023.
+\item
+\textbf{\href{https://ems.press/journals/mag/articles/9939904}{Smooth monotone stochastic variational inequalities and saddle point problems: A survey}} (Aleksandr Beznosikov, Boris Polyak, Eduard Gorbunov, Dmitry Kovalev, Alexander Gasnikov).
+\textit{European Mathematical Society Magazine}, 2023.
+\item
+\textbf{\href{https://proceedings.mlr.press/v202/metelev23a.html}{Is consensus acceleration possible in decentralized optimization over slowly time-varying networks?}} (Dmitry Metelev, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov).
+\textit{International Conference on Machine Learning}, 2023.
+\item
+\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2022.2117355}{Stochastic distributed learning with gradient quantization and double-variance reduction}} (Samuel Horvath, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik, Sebastian Stich).
+\textit{Optimization Methods and Software}, 2023.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/883f66687a521536c505f9b2fbdcbf1e-Abstract-Conference.html}{Accelerated primal-dual gradient method for smooth and convex-concave saddle-point problems with bilinear coupling}} (Dmitry Kovalev, Alexander Gasnikov, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/88c3c482430a62d35e03926a22e4b67e-Abstract-Conference.html}{Communication acceleration of local gradient methods via an accelerated primal-dual algorithm with an inexact prox}} (Abdurakhmon Sadiev, Dmitry Kovalev, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/c959bb2cb164d37569a17fa67494d69a-Abstract-Conference.html}{Optimal algorithms for decentralized stochastic variational inequalities}} (Dmitry Kovalev, Aleksandr Beznosikov, Abdurakhmon Sadiev, Michael Persiianov, Peter Richtarik, Alexander Gasnikov).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/d88f6f81e1aaf606776ffdd06fdf24ef-Abstract-Conference.html}{Optimal gradient sliding and its application to optimal distributed optimization under similarity}} (Dmitry Kovalev, Aleksandr Beznosikov, Ekaterina Borodich, Alexander Gasnikov, Gesualdo Scutari).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/e56f394bbd4f0ec81393d767caa5a31b-Abstract-Conference.html}{The first optimal acceleration of high-order methods in smooth convex optimization}} (Dmitry Kovalev, Alexander Gasnikov).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2022/hash/5e2ed801f62102f531d109d7c6e1b62f-Abstract-Conference.html}{The first optimal algorithm for smooth and strongly-convex-strongly-concave minimax optimization}} (Dmitry Kovalev, Alexander Gasnikov).
+\textit{Advances in Neural Information Processing Systems}, 2022.
+\item
+\textbf{\href{http://crm-en.ics.org.ru/uploads/crmissues/crm_2023_02/22_tominin.pdf}{Accelerated variance-reduced methods for saddle-point problems}} (Ekaterina Borodich, Vladislav Tominin, Yaroslav Tominin, Dmitry Kovalev, Alexander Gasnikov, Pavel Dvurechensky).
+\textit{EURO Journal on Computational Optimization}, 2022.
+\item
+\textbf{\href{https://proceedings.mlr.press/v151/salim22a.html}{An optimal algorithm for strongly convex minimization under affine constraints}} (Adil Salim, Laurent Condat, Dmitry Kovalev, Peter Richtarik).
+\textit{International Conference on Artificial Intelligence and Statistics}, 2022.
+\item
+\textbf{IntSGD: Adaptive floatless compression of stochastic gradients} (Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtarik).
+\textit{International Conference on Learning Representations}, 2022.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper/2021/hash/bc37e109d92bdc1ea71da6c919d54907-Abstract.html}{Lower bounds and optimal algorithms for smooth and strongly convex decentralized optimization over time-varying networks}} (Dmitry Kovalev, Elnur Gasanov, Alexander Gasnikov, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2021.
+\item
+\textbf{\href{https://proceedings.mlr.press/v130/kovalev21a.html}{A linearly convergent algorithm for decentralized optimization: Sending less bits for free!}} (Dmitry Kovalev, Anastasia Koloskova, Martin Jaggi, Peter Richtarik, Sebastian Stich).
+\textit{International Conference on Artificial Intelligence and Statistics}, 2021.
+\item
+\textbf{\href{http://proceedings.mlr.press/v139/kovalev21a}{ADOM: accelerated decentralized optimization method for time-varying networks}} (Dmitry Kovalev, Egor Shulgin, Peter Richtarik, Alexander V Rogozin, Alexander Gasnikov).
+\textit{International Conference on Machine Learning}, 2021.
+\item
+\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov).
+\textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.
+\item
+\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin).
+\textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{Linearly converging error compensated SGD}} (Eduard Gorbunov, Dmitry Kovalev, Dmitry Makarenko, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2020.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{Optimal and practical algorithms for smooth and strongly convex decentralized optimization}} (Dmitry Kovalev, Adil Salim, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2020.
+\item
+\textbf{\href{https://proceedings.mlr.press/v117/kovalev20a.html}{Don’t jump through hoops and remove those loops: SVRG and Katyusha are better without the outer loop}} (Dmitry Kovalev, Samuel Horvath, Peter Richtarik).
+\textit{Algorithmic Learning Theory}, 2020.
+\item
+\textbf{\href{https://link.springer.com/article/10.1134/S0965542520110020}{Accelerated methods for saddle-point problem}} (Mohammad S Alkousa, Alexander Vladimirovich Gasnikov, Darina Mikhailovna Dvinskikh, Dmitry A Kovalev, Fedor Sergeevich Stonyakin).
+\textit{Computational Mathematics and Mathematical Physics}, 2020.
+\item
+\textbf{\href{http://proceedings.mlr.press/v108/mishchenko20a}{Revisiting stochastic extragradient}} (Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtarik, Yura Malitsky).
+\textit{International Conference on Artificial Intelligence and Statistics}, 2020.
+\item
+\textbf{\href{https://proceedings.mlr.press/v119/li20g.html}{Acceleration for compressed gradient descent in distributed and federated optimization}} (Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtarik).
+\textit{International Conference on Machine Learning}, 2020.
+\item
+\textbf{\href{http://proceedings.mlr.press/v119/malinovskiy20a.html}{From local SGD to local fixed-point methods for federated learning}} (Grigory Malinovskiy, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtarik).
+\textit{International Conference on Machine Learning}, 2020.
+\item
+\textbf{\href{https://proceedings.mlr.press/v119/hanzely20b.html}{Variance reduced coordinate descent with acceleration: New method with a surprising application to finite-sum problems}} (Filip Hanzely, Dmitry Kovalev, Peter Richtarik).
+\textit{International Conference on Machine Learning}, 2020.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/bc6dc48b743dc5d013b1abaebd2faed2-Abstract.html}{RSN: randomized subspace Newton}} (Robert Gower, Dmitry Kovalev, Felix Lieder, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2019.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/6a8018b3a00b69c008601b8becae392b-Abstract.html}{Stochastic proximal langevin algorithm: Potential splitting and nonasymptotic rates}} (Adil Salim, Dmitry Kovalev, Peter Richtarik).
+\textit{Advances in Neural Information Processing Systems}, 2019.
+\item
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2018/hash/e721a54a8cf18c8543d44782d9ef681f-Abstract.html}{Stochastic spectral and conjugate descent methods}} (Dmitry Kovalev, Peter Richtarik, Eduard Gorbunov, Elnur Gasanov).
+\textit{Advances in Neural Information Processing Systems}, 2018.
+\item
+\textbf{\href{http://crm-en.ics.org.ru/journal/article/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev).
+\textit{Computer research and modeling}, 2018.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \textbf{Decentralized Optimization over Time-varying Graphs: a Survey} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{}{\color{linkcolour}Aleksander Beznosikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2210.09719}{\em \color{black}arXiv preprint (October 2022)}
-\item \textbf{Smooth Monotone Stochastic Variational Inequalities and Saddle Point Problems - Survey} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{https://sites.google.com/site/lab7polyak/}{\color{linkcolour}Boris Polyak}, \href{https://eduardgorbunov.github.io}{\color{linkcolour}Eduard Gorbunov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2208.13592}{\em \color{black}arXiv preprint (August 2022)}
-\item \textbf{On Scaled Methods for Saddle Point Problems} (\href{https://anbeznosikov.github.io}{\color{linkcolour}Aleksandr Beznosikov}, \href{}{\color{linkcolour}Aibek Alanov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2206.08303}{\em \color{black}arXiv preprint (June 2022)}
-\item \textbf{Decentralized Saddle-Point Problems with Different Constants of Strong Convexity and Strong Concavity} (\href{}{\color{linkcolour}Dmitriy Metelev}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2206.00090}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{Decentralized Computation of Wasserstein Barycenter over Time-Varying Networks} (\href{https://scholar.google.com/citations?user=v6tuw7IAAAAJ}{\color{linkcolour}Olga Yufereva}, \href{}{\color{linkcolour}Michael Persiianov}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/2205.15669}{\em \color{black}arXiv preprint (May 2022)}
-\item \textbf{Decentralized Distributed Optimization for Saddle Point Problems} (\href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}, \href{https://anbeznosikov.github.io}{\color{linkcolour}Alexander Beznosikov}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{http://wias-berlin.de/people/dvureche/}{\color{linkcolour}Pavel Dvurechensky}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}), \href{https://arxiv.org/abs/2102.07758}{\em \color{black}arXiv preprint (February 2021)}
-\item \textbf{Fast Linear Convergence of Randomized BFGS} (\href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://gowerrobert.github.io}{\color{linkcolour}Robert M.
-Gower}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://scholar.google.com/citations?user=sEjyzkgAAAAJ}{\color{linkcolour}Alexander Rogozin}), \href{https://arxiv.org/abs/2002.11337}{\em \color{black}arXiv preprint (February 2020)}
-\item \textbf{Distributed Fixed Point Methods with Compressed Iterates} (\href{https://scholar.google.com/citations?user=gyiubRkAAAAJ}{\color{linkcolour}Selim Chraibi}, \href{https://rka97.github.io}{\color{linkcolour}Ahmed Khaled}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}, \href{https://richtarik.org}{\color{linkcolour}Peter Richtarik}, \href{https://adil-salim.github.io}{\color{linkcolour}Adil Salim}, \href{https://mtakac.com}{\color{linkcolour}Martin Takac}), \href{https://arxiv.org/abs/1912.09925}{\em \color{black}arXiv preprint (December 2019)}
-\item \textbf{Accelerated methods for composite non-bilinear saddle point problem} (\href{https://scholar.google.com/citations?user=dJgWojUAAAAJ}{\color{linkcolour}Mohammad Alkousa}, \href{https://scholar.google.com/citations?user=5ILnTRsAAAAJ}{\color{linkcolour}Darina Dvinskikh}, \href{https://www.researchgate.net/profile/Fedor_Stonyakin}{\color{linkcolour}Fedor Stonyakin}, \href{https://scholar.google.ru/citations?user=AmeE8qkAAAAJ}{\color{linkcolour}Alexander Gasnikov}, \href{https://www.dmitry-kovalev.com}{\color{linkcolour}Dmitry Kovalev}), \href{https://arxiv.org/abs/1906.03620}{\em \color{black}arXiv preprint (December 2019)}
+\item
+\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2407.02020}, 2024.
+\item
+\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
+\textit{arXiv preprint arXiv:2405.18031}, 2024.
+\item
+\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized Finite-Sum Optimization over Time-Varying Networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2402.02490}, 2024.
+\item
+\textbf{\href{https://arxiv.org/abs/2307.12946}{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2307.12946}, 2023.
+\item
+\textbf{\href{https://arxiv.org/abs/2212.14439}{An optimal algorithm for strongly convex min-min optimization}} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky).
+\textit{arXiv preprint arXiv:2212.14439}, 2022.
+\item
+\textbf{\href{https://arxiv.org/abs/2206.08303}{On scaled methods for saddle point problems}} (Aleksandr Beznosikov, Aibek Alanov, Dmitry Kovalev, Martin Takac, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2206.08303}, 2022.
+\item
+\textbf{\href{https://arxiv.org/abs/2102.07758}{Decentralized distributed optimization for saddle point problems}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2102.07758}, 2021.
+\item
+\textbf{\href{https://arxiv.org/abs/2002.11337}{Fast linear convergence of randomized BFGS}} (Dmitry Kovalev, Robert M Gower, Peter Richtarik, Alexander Rogozin).
+\textit{arXiv preprint arXiv:2002.11337}, 2020.
+\item
+\textbf{\href{https://arxiv.org/abs/1912.09925}{Distributed fixed point methods with compressed iterates}} (Selim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtarik, Adil Salim, Martin Takac).
+\textit{arXiv preprint arXiv:1912.09925}, 2019.
+\item
+\textbf{\href{https://arxiv.org/abs/1912.01597}{Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates}} (Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik).
+\textit{arXiv preprint arXiv:1912.01597}, 2019.
 \end{enumerate}

### 2024-08-13 assets/js/main.js
trigger nav collapse

@@ -1,2 +1,9 @@
-$(document).ready(function(){
+$(document).ready(function () {
 });
+
+function navbar_link_click() {
+    let navbar_toggler = document.querySelector(".navbar-toggler");
+    if (getComputedStyle(navbar_toggler).getPropertyValue("display") != 'none') {
+        navbar_toggler.click();
+    }
+}

### 2024-08-14 CV2/papers.tex
arxiv button for preprints

@@
 \item
-\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov).
+\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov).
 \textit{arXiv preprint arXiv:2407.02020}, 2024.
 \item
-\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
+\textbf{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
 \textit{arXiv preprint arXiv:2405.18031}, 2024.
 \item
-\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized Finite-Sum Optimization over Time-Varying Networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov).
+\textbf{Decentralized Finite-Sum Optimization over Time-Varying Networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov).
 \textit{arXiv preprint arXiv:2402.02490}, 2024.
 \item
-\textbf{\href{https://arxiv.org/abs/2307.12946}{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov).
+\textbf{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov).
 \textit{arXiv preprint arXiv:2307.12946}, 2023.
 \item
-\textbf{\href{https://arxiv.org/abs/2212.14439}{An optimal algorithm for strongly convex min-min optimization}} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky).
-\textit{arXiv preprint arXiv:2212.14439}, 2022.
+\textbf{An optimal algorithm for strongly convex min-min optimization} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky). \textit{arXiv preprint arXiv:2212.14439}, 2022.
 \item
-\textbf{\href{https://arxiv.org/abs/2206.08303}{On scaled methods for saddle point problems}} (Aleksandr Beznosikov, Aibek Alanov, Dmitry Kovalev, Martin Takac, Alexander Gasnikov).
-\textit{arXiv preprint arXiv:2206.08303}, 2022.
+\textbf{On scaled methods for saddle point problems} (Aleksandr Beznosikov, Aibek Alanov, Dmitry Kovalev, Martin Takac, Alexander Gasnikov). \textit{arXiv preprint arXiv:2206.08303}, 2022.
 \item
-\textbf{\href{https://arxiv.org/abs/2102.07758}{Decentralized distributed optimization for saddle point problems}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
+\textbf{Decentralized distributed optimization for saddle point problems} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
 \textit{arXiv preprint arXiv:2102.07758}, 2021.
 \item
-\textbf{\href{https://arxiv.org/abs/2002.11337}{Fast linear convergence of randomized BFGS}} (Dmitry Kovalev, Robert M Gower, Peter Richtarik, Alexander Rogozin).
-\textit{arXiv preprint arXiv:2002.11337}, 2020.
+\textbf{Fast linear convergence of randomized BFGS} (Dmitry Kovalev, Robert M Gower, Peter Richtarik, Alexander Rogozin). \textit{arXiv preprint arXiv:2002.11337}, 2020.
 \item
-\textbf{\href{https://arxiv.org/abs/1912.09925}{Distributed fixed point methods with compressed iterates}} (Selim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtarik, Adil Salim, Martin Takac).
+\textbf{Distributed fixed point methods with compressed iterates} (Selim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtarik, Adil Salim, Martin Takac).
 \textit{arXiv preprint arXiv:1912.09925}, 2019.
 \item
-\textbf{\href{https://arxiv.org/abs/1912.01597}{Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates}} (Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik).
-\textit{arXiv preprint arXiv:1912.01597}, 2019.
+\textbf{Stochastic Newton and cubic Newton methods with simple local linear-quadratic rates} (Dmitry Kovalev, Konstantin Mishchenko, Peter Richtarik). \textit{arXiv preprint arXiv:1912.01597}, 2019.
 \end{enumerate}

### 2024-11-28 CV2/papers.tex
update website

@@
 \item
-\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov).
+\textbf{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms} (Dmitry Kovalev, Ekaterina Borodich).
+\textit{arXiv preprint arXiv:2411.14601}, 2024.
+\item
+\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev).
 \textit{arXiv preprint arXiv:2407.02020}, 2024.
@@
 \item
-\textbf{Decentralized Finite-Sum Optimization over Time-Varying Networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov).
+\textbf{Decentralized finite-sum optimization over time-varying networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov, Dmitry Kovalev).
 \textit{arXiv preprint arXiv:2402.02490}, 2024.

### 2024-11-28 CV2/papers.tex
update CV

--- 2024-08-13 CV2/papers.tex
@@
 \item
-\textbf{IntSGD: Adaptive floatless compression of stochastic gradients} (Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtarik).
+\textbf{\href{https://arxiv.org/abs/2102.08374}{IntSGD: Adaptive floatless compression of stochastic gradients}} (Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtarik).
 \textit{International Conference on Learning Representations}, 2022.
@@
 \item
-\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov).
+\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Dmitry Kovalev, Ekaterina Borodich).
+\textit{arXiv preprint arXiv:2411.14601}, 2024.
+\item
+\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev).
 \textit{arXiv preprint arXiv:2407.02020}, 2024.
@@
 \item
-\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized Finite-Sum Optimization over Time-Varying Networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov).
+\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized finite-sum optimization over time-varying networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov, Dmitry Kovalev).
 \textit{arXiv preprint arXiv:2402.02490}, 2024.

### 2025-03-21 CV2/papers.tex
update papers

@@
 \begin{enumerate}
+\item
+\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev).
+\textit{International Conference on Learning Representations}, 2025.
+\item
+\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
+\textit{Advances in Neural Information Processing Systems}, 2024.
 \item
@@
 \textit{Optimization Methods and Software}, 2024.
+\item
+\textbf{Convex-Concave Interpolation and Application of PEP to the Bilinear-Coupled Saddle Point Problem} (Valery Krivchenko, Alexander Gasnikov, Dmitry Kovalev).
+\textit{Russian Journal of Nonlinear Dynamics}, 2024.
 \item
@@
 \item
-\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/6a8018b3a00b69c008601b8becae392b-Abstract.html}{Stochastic proximal langevin algorithm: Potential splitting and nonasymptotic rates}} (Adil Salim, Dmitry Kovalev, Peter Richtarik).
+\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/6a8018b3a00b69c008601b8becae392b-Abstract.html}{Stochastic proximal Langevin algorithm: Potential splitting and nonasymptotic rates}} (Adil Salim, Dmitry Kovalev, Peter Richtarik).
 \textit{Advances in Neural Information Processing Systems}, 2019.
@@
 \item
+\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}} (Dmitry Kovalev).
+\textit{arXiv preprint arXiv:2503.12645}, 2025.
+\item
+\textbf{\href{https://arxiv.org/abs/2503.06628}{On Solving Minimization and Min-Max Problems by First-Order Methods with Relative Error in Gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazari Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov).
+\textit{arXiv preprint arXiv:2503.06628}, 2025.
+\item
 \textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Dmitry Kovalev, Ekaterina Borodich).
 \textit{arXiv preprint arXiv:2411.14601}, 2024.
-\item
-\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev).
-\textit{arXiv preprint arXiv:2407.02020}, 2024.
-\item
-\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
-\textit{arXiv preprint arXiv:2405.18031}, 2024.
 \item

### 2025-07-10 CV2/papers.tex
new papers

@@
 \textit{International Conference on Learning Representations}, 2025.
+\item
+\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Dmitry Kovalev).
+\textit{International Conference on Machine Learning}, 2025.
+\item
+\textbf{\href{https://arxiv.org/abs/2212.14439}{An Optimal Algorithm for Strongly Convex Min-Min Optimization}} (Dmitry Kovalev, Alexander Gasnikov, Grigory Malinovsky).
+\textit{Uncertainty in Artificial Intelligence}, 2025.
 \item
@@
 \item
-\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}} (Dmitry Kovalev).
+\textbf{\href{https://arxiv.org/abs/2506.23803}{SGD with Adaptive Preconditioning: Unified Analysis and Momentum Acceleration}} (Dmitry Kovalev). \textit{arXiv preprint arXiv:2506.23803}, 2025.
+\item
+\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding gradient orthogonalization for deep learning via non-euclidean trust-region optimization}} (Dmitry Kovalev).
 \textit{arXiv preprint arXiv:2503.12645}, 2025.
@@
 \textit{arXiv preprint arXiv:2503.06628}, 2025.
-\item
-\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Dmitry Kovalev, Ekaterina Borodich).
-\textit{arXiv preprint arXiv:2411.14601}, 2024.
 \item
@@
 \textit{arXiv preprint arXiv:2307.12946}, 2023.
-\item
-\textbf{\href{https://arxiv.org/abs/2212.14439}{An optimal algorithm for strongly convex min-min optimization}} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky).
-\textit{arXiv preprint arXiv:2212.14439}, 2022.
 \item

### 2025-07-18 CV2/papers.tex
add paper, semantic scholar api test

@@
 \item
-\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
+\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2024/hash/af10f27d0a48175e486a647c06c7a9c6-Abstract-Conference.html}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov).
 \textit{Advances in Neural Information Processing Systems}, 2024.
@@
 \item
-\textbf{\href{https://link.springer.com/content/pdf/10.1007/978-3-030-54621-2_860-1.pdf}{Decentralized Convex Optimization over Time-Varying Graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev).
+\textbf{\href{https://link.springer.com/rwe/10.1007/978-3-030-54621-2_860-1}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev).
 \textit{Encyclopedia of Optimization}, 2023.
@@
 \textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov).
-\textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.
+\textit{International Conference on Optimization and Applications}, 2021.
 \item
 \textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin).
-\textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.
+\textit{International Conference on Optimization and Applications}, 2021.
 \item
@@
 \item
-\textbf{\href{http://crm-en.ics.org.ru/journal/article/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev).
+\textbf{\href{https://crm-en.ics.org.ru/journal/article/references/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev).
 \textit{Computer research and modeling}, 2018.
@@
 \begin{enumerate}
+\item
+\textbf{\href{https://arxiv.org/abs/2507.09823}{Nesterov Finds GRAAL: Optimal and Adaptive Gradient Method for Convex Optimization}} (Ekaterina Borodich, Dmitry Kovalev).
+\textit{arXiv preprint arXiv:2507.09823}, 2025.
 \item

### 2025-10-27 CV2/talks.tex
cv
-
talks

@@
 \begin{enumerate}
+  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization}, Abu Dhabi, United Arab Emirates (October 2025)
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Innopolis University, Kazan, Russia (June 2025)
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://data-fusion.ru}{\em Data Fusion 2025 Conference}, Moscow, Russia (April 2025)
   \item {\bf Talk: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em Rising Stars in AI Symposium 2022}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (March 2022)
@@
   \item {\bf Talk/Poster: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021}, Online (July 2021)
-\item {\bf Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em Conference <<Optimization Without Borders>>}, Sirius University, Sochi, Russia (July 2021)
   \item {\bf Talk/Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em ICML 2021}, Online (July 2021)
+  \item {\bf Poster: ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks}, {\em Optimization Without Borders Conference}, Sirius University, Sochi, Russia (July 2021)
   \item {\bf Talk/Poster: A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!}, {\em AISTATS 2021}, Online (April 2021)
@@
   \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Data Science Summer School 2019}, Ecole Polytechnique, Paris, France (June 2019)
-\item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
-\item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Weekly Seminar <<Automatic control and Optimization Theory>>}, Institute for Control Problems, Moscow, Russia (March 2019)
-\item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Seminar <<Modern Optimization Methods>>}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
+  \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
+  \item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Automatic control and Optimization Theory Weekly Seminar}, Institute for Control Problems, Moscow, Russia (March 2019)
+  \item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Modern Optimization Methods Seminar}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
   \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em NeurIPS 2018}, Montreal, Canada (December 2018)
   \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Optimization and Big Data Workshop}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (June 2018)
-\item {\bf Poster: Stochastic Spectral Descent Methods}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (February 2018)
+  \item {\bf Poster: Stochastic Spectral Descent Methods}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (February 2018)
 \end{enumerate}

### 2025-11-18 CV3/CV.tex
CV-ru

--- 2022-03-23 CV2/CV.tex
@@
 \documentclass[a4paper,10pt]{article} % Default font size and paper size
-%\usepackage[T1]{fontenc}
-%\usepackage[utf8]{inputenc}
 \usepackage{fontspec} % For loading fonts
 
-%\setmainfont{[Fontin-Regular.otf]}
 \defaultfontfeatures{Mapping=tex-text}
-% \setmainfont{[Fontin-Regular.otf]} % Main document font
-% \setmainfont[SmallCapsFont = Fontin-SmallCaps.otf]{[Fontin-Regular.otf]} % Main document font
-\setmainfont{Fontin-Regular.otf}[
-BoldFont       = Fontin-Bold.otf ,
-ItalicFont     = Fontin-Italic.otf ,
-SmallCapsFont  = Fontin-SmallCaps.otf ]
 
+% \setmainfont{Fontin-Regular.otf}[
+%   BoldFont       = Fontin-Bold.otf ,
+%   ItalicFont     = Fontin-Italic.otf ,
+% SmallCapsFont  = Fontin-SmallCaps.otf ]
+
+\setmainfont{FontinSans_Cyrillic_R_46b.otf}[
+  BoldFont       = FontinSans_Cyrillic_B_46b.otf,
+  ItalicFont     = FontinSans_Cyrillic_I_46b.otf ,
+  SmallCapsFont  = FontinSans_Cyrillic_SC_46b.otf
+]
 \usepackage{xunicode,xltxtra,url,parskip} % Formatting packages
@@
 
-\par{\centering{\Huge Dmitry Kovalev}\bigskip\par} % Your name
+\par{\centering{\Huge Дмитрий Ковалев}\bigskip\par} % Your name
 
@@
 
+\input{awards.tex}
+
 \input{papers.tex}
 
+\input{talks.tex}
+
+\input{teaching.tex}
+
+\vspace{2em}
 \input{date.tex}

### 2025-11-18 CV3/awards.tex
CV-ru

--- 2022-03-23 CV2/awards.tex
@@
 	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
+	\item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
 	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
+	\item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
 	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018

### 2025-11-18 CV3/general.tex
CV-ru

--- 2023-10-15 CV2/general.tex
@@
-\section{Personal Data}
+\section{Личные данные}
 
 \begin{tabular}{rl}
-	\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
-	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
-	\textsc{Phone} &  +32 499 34 93 21 (Belgium)\\
-	\textsc{Phone} & +7 905 719 06 98 (Russia)\\
+  \textsc{Электронная почта} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
+  \textsc{Веб-сайт} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
+  \textsc{Телефон} & +7 905 719 06 98\\
   \textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
   \textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
-	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}
+  %   \textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}
 
@@
 
-\section{Positions}
+\section{Опыт работы}
 \begin{tabular}{rl}
-	\textsc{2021-Now}& Research Intern\\
-	&Research Center for Trusted Artificial Intelligence\\
-	&\textbf{\href{https://www.ispras.ru/en/}{\color{black}Ivannikov Institute for System Programming}}, Moscow, Russia\\
-	\textsc{2022-2023}& Postdoctoral Researcher\\
-	& \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Université catholique de Louvain}}, Louvain-la-Neuve, Belgium\\
-	\textsc{2022-2023}& Researcher\\
-	&Laboratory of Advanced Combinatorics and Network Applications\\
-	&\textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia
+  \textsc{2023-н.в.}& Ведущий исследователь\\
+  &\textbf{\href{https://research.yandex.com}{\color{black}Яндекс}}, Москва, Россия\\
+  \textsc{2022-2023}& Постдокторантура\\
+  & \textbf{\href{https://uclouvain.be/en/index.html}{\color{black}Католический университет Лувена}}, Лувен-ла-Нёв, Бельгия\\
+  \textsc{2021-2023}& Стажер-исследователь\\
+  &Исследовательский центр доверенного искусственного интеллекта\\
+  &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
+  \\&Москва, Россия\\
+  \textsc{2022}& Исследователь\\
+  &Лаборатория продвинутой комбинаторики и сетевых приложений\\
+  &\textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия
 \end{tabular}
@@
 
-\section{Skills}
+\section{Навыки}
 
 \begin{tabular}{rl}
-	\textsc{Programming} & C/C++, Python,
-	Algorithms and Data Structures (\href{https://codeforces.com/profile/Dakovalev1}{Codeforces master}), JAX,\\
-	&PyTorch; \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
-	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
-	\textsc{Computer} & macOS, LaTeX, Git\\
-		\textsc{Languages} & English (Advanced), Russian (Native)
+  \textsc{Программирование} & C/C++, Python, JAX, PyTorch,
+  \\&Алгоритмы и структуры данных (\href{https://codeforces.com/profile/Dakovalev1}{Мастер Codeforces})\\
+  %   \\&\textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
+  \textsc{Математика} & Математический анализ, Линейная алгебра,\\
+  &Теория вероятностей и статистика, Выпуклый Анализ\\
+  \textsc{Компьютер} & macOS, LaTeX, Git\\
+  \textsc{Языки} & Русский, Английский
 \end{tabular}

### 2025-11-18 CV3/talks.tex
CV-ru

--- 2022-03-24 CV2/talks.tex
@@
 \begin{enumerate}
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, {\em Traditional School (Control, Information and Optimization)}, Innopolis University, Kazan, Russia (June 2025)
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, {\em Data Fusion 2025 Conference}, Moscow, Russia (April 2025)
   \item {\bf Talk: Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks}, {\em Rising Stars in AI Symposium 2022}, King Abdullah University of Science and Technology, Thuwal, Saudi Arabia (March 2022)
@@
   \item {\bf Poster: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Traditional School (Control, Information and Optimization)}, Higher School of Economics Study Center, Voronovo, Russia (June 2019)
-\item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Weekly Seminar <<Automatic control and Optimization Theory>>}, Institute for Control Problems, Moscow, Russia (March 2019)
-\item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Seminar <<Modern Optimization Methods>>}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
+  \item {\bf Talk: Stochastic Spectral Descent Methods}, {\em Automatic control and Optimization Theory Weekly Seminar}, Institute for Control Problems, Moscow, Russia (March 2019)
+  \item {\bf Talk: Stochastic Distributed Learning with Gradient Quantization and Variance Reduction}, {\em Modern Optimization Methods Seminar}, Moscow Institute of Physics and Technology, Moscow, Russia (March 2019)
   \item {\bf Poster: Stochastic Spectral Descent Methods}, {\em NeurIPS 2018}, Montreal, Canada (December 2018)

### 2025-11-18 CV2/talks.tex

@@
 \begin{enumerate}
-  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization}, Abu Dhabi, United Arab Emirates (October 2025)
+  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization 2025}, Abu Dhabi, United Arab Emirates (October 2025)
   \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://ssopt.org}{\em Traditional School (Control, Information and Optimization)}, Innopolis University, Kazan, Russia (June 2025)

### 2025-11-18 CV3/awards.tex
-

--- 2022-03-23 CV2/awards.tex
@@
-\section{Honors and Awards}
+\section{Награды}
 \hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
 \begin{enumerate}
-	\item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
-	\item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
-	\item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
-	\item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
-	\item \textbf{Abramov’s Fund Scholarship for Excellence in Study}, Moscow Institute of Physics and Technology, 2015-2017
-	\item \textbf{Asian Physics Olympiad (APhO) 2014, Honourable Mention}, Singapore (participated as a member of Russian national team)
+  \item \href{https://ai-awards.ru/}{\textbf{Национальная премия ``Лидеры ИИ'' 2025}}, Конференция ``AI Journey''
+  \item \href{https://media.innopolis.university/news/yandex-research-employee-receives-polyak-prize/}{\textbf{Премия имени Б.Т. Поляка для молодых учёных 2025}}, Университет Иннополиc
+  \item  \textbf{Студенческая премия за отличные успехи в науке}, Научно-технологический университет имени короля Абдаллы, 2021
+  \item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Лучшая студенческая работа воркшопа FL-ICML 2021}}
+  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Научная премия Яндекса 2021}}, Яндекс
+    %   \item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
+  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Научная премия Яндекса 2020}}, Яндекс
+    %   \item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018
+  \item \textbf{Стипендия Абрамова за отличные успехи в учебе}, Московский физико-технический институт, 2015-2017
+  \item \textbf{Азиатская физическая олимпиада (APhO) 2014, похвальная грамота}, Сингапур
 
   \item \textbf{Russian President’s Scholarship for High School Sudents}, given for prize-winning at final round of All-Russian School Olympiads, 2012-2014
-	\item \textbf{Moscow Governor’s Scholarship for High School Sudents}, given for prize-winning at region and final rounds of All-Russian School Olympiads, 2012-2014
+    %   \item \textbf{Moscow Governor’s Scholarship for High School Sudents}, given for prize-winning at region and final rounds of All-Russian School Olympiads, 2012-2014
 
-	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg, 2014
-	\item \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow, 2014
-	\item \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow, 2014
+  \item \textbf{Призер заключительного этапа Всеросийской олимпиады школьников по физике}, Санкт-Петербург, 2014
 
-	\item \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok, 2013
-	\item \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk, 2012
+  \item \textbf{Победитель регионального этапа Всеросийской олимпиады школьников по информатике}, Москва, 2014
+  \item \textbf{Победитель регионального этапа Всеросийской олимпиады школьников по математике}, Москва, 2014
+  \item \textbf{Победитель заключительного этапа Всеросийской олимпиады школьников по физике}, Владивосток, 2013
+  \item \textbf{Призер заключительного этапа Всеросийской олимпиады школьников по физике}, Саранск, 2012
 \end{enumerate}

### 2025-11-18 CV3/general.tex
-

@@
   &Исследовательский центр доверенного искусственного интеллекта\\
-  &\textbf{\href{https://www.ispras.ru/en/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
-  \\&Москва, Россия\\
+  &\textbf{\href{https://www.ispras.ru/}{\color{black}Институт системного программирования им. В.П. Иванникова РАН}}
+  Москва, Россия\\
   \textsc{2022}& Исследователь\\
@@
 
-\section{Education}
+\section{Образование}
 \begin{tabular}{rl}
-  \textsc{2019-2022}& PhD in Computer Science\\
-  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
-  & Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-  & Thesis: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
-  & \hspace{\widthof{Thesis: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
-  & Defense Committee: -- External: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Yurii Nesterov}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Arkadi Nemirovsky}\\
-  &\hspace{\widthof{Defense Committee: }}-- Internal: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E.
+  \textsc{2019-2022}& Доктор философии (PhD) по компьютерным наукам\\
+  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}Научно-технологический университет имени короля Абдаллы}}, Тувал, Саудовская Аравия\\
+  & Руководитель: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
+  & Диссертация: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
+  & \hspace{\widthof{Диссертация: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
+  & Диссертационный совет: -- Внешний: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Юрий Нестеров}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Аркадий Немировский}\\
+  &\hspace{\widthof{Диссертационный совет: }}-- Внутренний: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E.
 Keyes}, \href{https://shao3wangdi.github.io}{Di Wang}, \href{https://scholar.google.com/citations?user=Vj2D8JQAAAAJ}{Matteo Parsani}\\
-  \textsc{2018-2021}& MS in Applied Mathematics and Physics\\
-  & \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
-  & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
-  \textsc{2018-2019}& MS in Computer Science\\
-  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
-  & Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
-  \textsc{2014-2018}& BS in Applied Mathematics and Physics\\
-  & \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
-  & Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
+  \textsc{2018-2021}& Магистр прикладных математики и физики\\
+  & \textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия\\
+  & Руководитель: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Александр Гасников}\\
+  \textsc{2018-2019}& Магистр компьютерных наук\\
+  & \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}Научно-технологический университет имени короля Абдаллы}}, Тувал, Саудовская Аравия\\
+  & Руководитель: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
+  \textsc{2014-2018}& Бакалавр прикладных математики и физики\\
+  & \textbf{\href{https://mipt.ru/}{\color{black}Московский физико-технический институт}}, Долгопрудный, Россия\\
+  & Руководитель: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Александр Гасников}\\
 \end{tabular}
 
-\section{Research Interests}
+\section{Научные интересы}
 %Optimization Algorithms, Distributed Optimization, Machine Learning
 \begin{tabular}{cl}
-  &  Optimization, Federated and Distributed Learning\\
-  &Machine Learning, Deep Learning
+  &  Оптимизация, Федеративное и распределенное обучение\\
+  & Машинное обучение, Глубокое обучение
 \end{tabular}

### 2025-11-25 CV2/awards.tex
CV

@@
 \section{Honors and Awards}
-\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
+\hypersetup{breaklinks,urlcolor=black,linkcolor=black}
 \begin{enumerate}
+  \item  \href{https://ai-awards.ru}{\textbf{National Award ``AI Leaders'' 2025}}, \href{https://aij.ru/en}{AI Journey 2025 Conference}
+  \item \href{https://media.innopolis.university/news/yandex-research-employee-receives-polyak-prize/}{\textbf{Boris Polyak Scientific Prize for Young Researchers 2025}}, Innopolis University
   \item  \textbf{CEMSE Student Research Excellence Award}, King Abdullah University of Science and Technology, 2021
   \item \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award at FL-ICML 2021 Workshop}}
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
+  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2021}, Yandex (highly selective: only 4 winners from Russia, Belarus, Kazakhstan)}
   \item {\bf  Annual PhD progress marked as Outstanding}, King Abdullah University of Science and Technology, 2019-2021
-	\item \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
+  \item \href{https://yandex.com/scholarships/#laureates}{\textbf{Ilya Segalovich Scientific Prize for Young Researchers 2020}, Yandex (highly selective: only 9 winners from Russia, Belarus, Kazakhstan)}
   \item {\bf Dean's Award}, given to top students accepted to King Abdullah University of Science and Technology, 2018

### 2025-12-15 CV2/papers.tex
update website

@@
 \item
-\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Dmitry Kovalev).
+\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Alexander Gasnikov, Dmitry Kovalev).
 \textit{International Conference on Machine Learning}, 2025.
+\item
+\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2023.2280062}{Decentralized saddle point problems via non-Euclidean mirror prox}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
+\textit{Optimization Methods and Software}, 2025.
+\item
+\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2025.2545846}{Near-optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov).
+\textit{Optimization Methods and Software}, 2025.
 \item
@@
 \item
-\textbf{\href{https://www.tandfonline.com/doi/abs/10.1080/10556788.2023.2280062}{Decentralized saddle point problems via non-Euclidean mirror prox}} (Alexander Rogozin, Aleksandr Beznosikov, Darina Dvinskikh, Dmitry Kovalev, Pavel Dvurechensky, Alexander Gasnikov).
-\textit{Optimization Methods and Software}, 2024.
-\item
 \textbf{Convex-Concave Interpolation and Application of PEP to the Bilinear-Coupled Saddle Point Problem} (Valery Krivchenko, Alexander Gasnikov, Dmitry Kovalev).
@@
 \item
-\textbf{\href{https://link.springer.com/rwe/10.1007/978-3-030-54621-2_860-1}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev).
+\textbf{\href{https://arxiv.org/abs/2210.09719}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev).
 \textit{Encyclopedia of Optimization}, 2023.
@@
 \item
+\textbf{\href{https://arxiv.org/abs/2511.11466}{Non-Euclidean SGD for Structured Optimization: Unified Analysis and Improved Rates}} (Dmitry Kovalev, Ekaterina Borodich).
+\textit{arXiv preprint arXiv:2511.11466}, 2025.
+\item
 \textbf{\href{https://arxiv.org/abs/2507.09823}{Nesterov Finds GRAAL: Optimal and Adaptive Gradient Method for Convex Optimization}} (Ekaterina Borodich, Dmitry Kovalev).
@@
 \item
-\textbf{\href{https://arxiv.org/abs/2503.06628}{On Solving Minimization and Min-Max Problems by First-Order Methods with Relative Error in Gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazari Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov).
+\textbf{\href{https://arxiv.org/abs/2503.06628}{On solving minimization and min-max problems by first-order methods with relative error in gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazarii Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov).
 \textit{arXiv preprint arXiv:2503.06628}, 2025.
@@
 \textit{arXiv preprint arXiv:2402.02490}, 2024.
-\item
-\textbf{\href{https://arxiv.org/abs/2307.12946}{Optimal algorithm with complexity separation for strongly convex-strongly concave composite saddle point problems}} (Ekaterina Borodich, Georgiy Kormakov, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Gasnikov).
-\textit{arXiv preprint arXiv:2307.12946}, 2023.
 \item

### 2025-12-15 CV2/talks.tex
CV update

@@
 \begin{enumerate}
+  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://www.mathnet.ru/eng/conf2402}{\em Mathematical Foundations of Artificial Intelligence Seminar}, Steklov Mathematical Institute, Moscow, Russia (November 2025)
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://cs.hse.ru/en/iai/hdilab/seminar/}{\em HDI Lab Strctural LEarning Seminar}, Higher School of Econimics, Moscow, Russia (December 2025)
   \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization 2025}, Abu Dhabi, United Arab Emirates (October 2025)

### 2025-12-18 CV2/talks.tex
-

--- 2025-11-18 CV2/talks.tex
@@
 \begin{enumerate}
+  \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://www.mathnet.ru/eng/conf2402}{\em Mathematical Foundations of Artificial Intelligence Seminar}, Steklov Mathematical Institute, Moscow, Russia (November 2025)
+  \item {\bf Talk: Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}, \href{https://cs.hse.ru/en/iai/hdilab/seminar/}{\em HDI Lab Structural Learning Seminar}, Higher School of Economics, Moscow, Russia (December 2025)
   \item {\bf Talk: Recent Advances in Adaptive Convex Optimization}, \href{https://icomp.cc}{\em International Conference on Computational Optimization 2025}, Abu Dhabi, United Arab Emirates (October 2025)
